---
title: "23 - 011 ALAN x HERBIVORY"
author: "VINCENT GROGNUZ"
date: "30/11/2023"
output:
  html_document: default
  pdf_document: default
---

# 00 / HOME DIRECTORY 

```{r 00 HOME DIRECTORY, echo = TRUE, warning = FALSE, message = FALSE}
# REMOVE ALL OBJECT FROM R-WORKING SPACE
rm(list=ls()) 

# EMPTY THE GARBAGE
gc()

# MAKE A NEW LOCAL DIRECTORY ON YOUR MACHINE IN WHICH R WILL LOOK FOR THIS ANALYSIS AND WILL EXPORT GRAPHS & CO.
DIRECTORY = "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/06_ANALYSIS/2023/"
HOME = paste0(DIRECTORY, "01_ALAN x HERBIVORY/OUTPUT")
rm(DIRECTORY)

# CHECK IF THAT DIRECTORY EXIST
file.exists(HOME)

# MAKE HOME OUR WORK DIRECTORY, THE DEFAULT FOLDER IN WHICH R WILL LOOK
setwd(HOME)
```

# 00 / LIBRARY   

```{r 00 LIBRARY, echo = TRUE, warning = FALSE, message = FALSE}
# I NEVER REMEMBER WHICH PACKAGES I USE. I ALWAYS LOAD THEM ALL....

library("RColorBrewer")
library("stringr")
# library("stringi")
# library("tidyverse")
library("ggplot2")
library("ggpubr")
library("data.table")
library("dplyr")
# library("plyr")           # LOAD MULTIPLE CSV TABLES
# library("readr")
library("lubridate")
library("wesanderson")  # Color palettes 1
library("RColorBrewer") # Color palettes 2
# library("maptools")     # Import .shp and work with it
# library("spatstat")     # Import .shp and work with it
# library("rgdal")        # Deal with .shp
# library("rgeos")        # Deal with .shp
# library("installr")
# library("terra")
# library("raster")
library("gridExtra")
library("grid")
library("gridExtra")    # MERGE DIFFERENT GGPLOT
library("ggcorrplot")   # PEARSON CORRELATION PLOT
library("reshape2")
# library("rmarkdown")
# library("ggfortify")    # GLM OUTPUT WITH GGPLOT
library("pscl")         # ZERO INFLATED MODELS
# library("lmtest")       # LOGLIKELIHOOD TEST
# library("MASS")         # GLM.NB
library("lme4")         # glmer
# library("nlme")         # lme
# library("glmmADMB")
library("GLMMadaptive")
# library("FactoMineR")   # Compute MCA
# library("factoextra")   # Visualize MCA
# library("piecewiseSEM")
# library("lavaan")
# library("semEff")
library("ggpattern")
library("rlist")
library("Hmisc")
library("piecewiseSEM")
library("multcompView")
library("knitr")
library("arm")
library("stargazer")
library("png")
library("patchwork")
library("gtsummary")
library("broom.mixed")
library("car")
# library("ggstats")
library("gt")
library("webshot2")
library("sjPlot")
library("glmmTMB")
library("ggsurvfit")
library("survival")

```

# 00 / LOAD DATA 

```{r 00 LOAD DATA, echo = TRUE, warning = FALSE, message = FALSE}

# LOAD DATA
###########

# STUDY SITES
#------------
STUDY_SITES <- read.csv(
  "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/07_GIS/03_FIELDS/2023/2023_STUDY SITES.csv",
  header = F)

STUDY_SITES.ls <- unique(STUDY_SITES$V1)

LIT.SITE <- c("QUAIL", "DEER", "EAGLE", "GRASS SNAKE", "HORNET", "MARTEN", "TOAD", "WOODPECKER")
DARK.SITE <- c("UPUPA", "CHAMOIS", "PEREGRINE", "LIZARD", "ANTS", "BADGER", "NEWT", "YELLOWHAMMER", "YELLOW HAMMER")

LIT.SITE.22 <- c("ANTS", "DEER", "OAK", "PIZZA", "RABBIT", "STORK")
DARK.SITE.22 <- c("BADGER", "VOLE", "JUNGLE", "FOX", "TRAIN II", "KINGFISHER", "ZZ_ANTS II", "ZZ_BADGER II", 
                  "ZZ_BADGER III", "ZZ_DEER II", "ZZ_DEER III", "ZZ_DEER IV", "ZZ_FOX II", "ZZ_KINGFISHER II", 
                  "ZZ_KINGFISHER III", "ZZ_PIZZA II", "ZZ_VULLY", "ZZ_VULLY II")

# With coordinates
DATADIR = "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2022/"
STUDY_SITES.coord <- read.csv(paste0(DATADIR,  "00_STUDY SITES/220722_STUDY SITES_COORD.csv"))

# PLANT LIST
#-----------
PLANTS <- read.csv(
  "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/07_GIS/03_FIELDS/2023/2023_PLANTS.csv",
  header = F)

PLANTS.ls <- unique(PLANTS$V1)

# ABIOTIC - METEO SUISSE PAYERNE
#-------------------------------
ABIOTIC.22 <- read.csv(
  "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2022/2022_ZZ_ABIOTIC/2022_ABIOTIC_PAYERNE.csv",
  header = T)

ABIOTIC.23 <- read.csv(
  "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_ZZ_ABIOTIC/2023_ABIOTIC_PAYERNE.csv",
  header = T)

ABIOTIC <- rbind(ABIOTIC.22, ABIOTIC.23)
rm(ABIOTIC.22, ABIOTIC.23)

# Mean temperature last 12 hours
ABIOTIC$TEMP_12H <- NA

for(i in (13:nrow(ABIOTIC))){
  
  # i <- 15
  
  i.ABIOTIC <- ABIOTIC[((i-11):i),]
  ABIOTIC$TEMP_12H[i] <- round(mean(i.ABIOTIC$TEMP_2M), 1)
  
}

rm(i.ABIOTIC, i)

# SLUGLINGS
#----------
DATADIR = "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/"
DEROCERAS <- read.csv(paste0(DATADIR,  "2023_ZZ_SLUGS WEIGHT/slug_weights_rearranged.csv"))
rm(DATADIR)

DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_H_SLUGS/"
ARYON <- read.csv(paste0(DATADIR,  "2023_H_SLUGS_LAST EXPORT.csv"), sep = ";")
rm(DATADIR)

DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_H_SLUGS/2024_BEHAVIOUR/SHIFT TABLES/"

DARK.WEEK02 <- read.csv(paste0(DATADIR,  "DARK.WEEK02.csv"))
DARK.WEEK03 <- read.csv(paste0(DATADIR,  "DARK.WEEK03.csv"))
DARK.WEEK04 <- read.csv(paste0(DATADIR,  "DARK.WEEK04.csv"))
DARK.WEEK05 <- read.csv(paste0(DATADIR,  "DARK.WEEK05.csv"))
DARK.WEEK06 <- read.csv(paste0(DATADIR,  "DARK.WEEK06.csv"))
LIT.WEEK02 <- read.csv(paste0(DATADIR,  "LIT.WEEK02.csv"))
LIT.WEEK03 <- read.csv(paste0(DATADIR,  "LIT.WEEK03.csv"))
LIT.WEEK04 <- read.csv(paste0(DATADIR,  "LIT.WEEK04.csv"))
LIT.WEEK05 <- read.csv(paste0(DATADIR,  "LIT.WEEK05.csv"))
LIT.WEEK06 <- read.csv(paste0(DATADIR,  "LIT.WEEK06.csv"))

SHIFT.TABLE <- rbind(DARK.WEEK02, DARK.WEEK03, DARK.WEEK04, DARK.WEEK05, DARK.WEEK06,
                     LIT.WEEK02, LIT.WEEK03, LIT.WEEK04, LIT.WEEK05, LIT.WEEK06)

rm(DARK.WEEK02, DARK.WEEK03, DARK.WEEK04, DARK.WEEK05, DARK.WEEK06, LIT.WEEK02, LIT.WEEK03, LIT.WEEK04, LIT.WEEK05, LIT.WEEK06)

# CENTAUREA POTS & HERBIVORY
#---------------------------

DATADIR = "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_E_HERBIVORY/CENTAUREA_POTS/"
CEPO <- read.csv(paste0(DATADIR,  "2023_E_HERBIVORY_FINAL_QUANTIFICATION-CLEAN.csv"))

rm(DATADIR)

# TRAITS IN WFS
#--------------
DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_C_TRAITS/TRAITS/00_ALL_TRAITS/"
TRAITS <- read.csv(paste0(DATADIR,  "C_240124_TRAITS.csv"))

# TRACKPLATES
#------------
DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2022/07_TRACK PLATES/"
TRACKS.22 <- read.csv(paste0(DATADIR,  "230501_TRACKPLATES.csv"))

DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_ZZ_TRACKPLATES/"
TRACKS.23 <- read.csv(paste0(DATADIR,  "2023_TRACKPLATES.csv"))

rm(DATADIR)

#-------------------------------------------------------------------------------------------------------------

# INTERACTION
#------------

DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/05_DATA/2023/2023_D_INTERACTIONS/FINAL (2022 + 2023)/"
INTERACTIONS <- read.csv(paste0(DATADIR,  "INTERACTION.csv"))

SAMPLING.ls <- sort(unique(paste0(INTERACTIONS$SAMPLING[INTERACTIONS$SAMP_TIME == "NIGHT"],
                             ".",
                             INTERACTIONS$SEGMENT[INTERACTIONS$SAMP_TIME == "NIGHT"])))

INTERACTIONS.ALL <- INTERACTIONS
INTERACTIONS <- INTERACTIONS[INTERACTIONS$ART_GROUP %in% c("SLUG", "SNAIL") & INTERACTIONS$SAMP_TIME == "NIGHT",] # 591

rm(DATADIR)
```

# 01.0 - SLUGLINGS / FORMAT & CO.

```{r 01.0 SLUGLINGS FORMAT AND CO, fig.width=10, message=FALSE, warning=FALSE}

# FORMAT DATA
#############

# numeric & co.
#--------------
DEROCERAS$weight <- as.numeric(DEROCERAS$weight)
ARYON$WEIGHT <- as.numeric(ARYON$WEIGHT)
names(DEROCERAS)[names(DEROCERAS) == "ï..batch"] <- "batch"

# Transform date into DOY [Day Of Year]
DEROCERAS$date <- as.Date(DEROCERAS$date, format = "%d-%m-%y", origin = "01/01/1970")
DEROCERAS$date_DOY <- yday(DEROCERAS$date)
 
ARYON$DATE <- as.Date(ARYON$DATE, format = "%d.%m.%Y", origin = "01/01/1970")
ARYON$DATE_DOY <- yday(ARYON$DATE)

# + 365  IF AFTER THE 1st OF JANUARY 2024
for(i in (1:nrow(ARYON))){
  
  ifelse(
    
    # ARGUMENT
    ARYON$DATE_DOY[i] < 250,
    
    # IF YES
    ARYON$DATE_DOY[i] <- ARYON$DATE_DOY[i] + 365,
    
    # IF NO
    ARYON$DATE_DOY[i] <- ARYON$DATE_DOY[i])

}


# WEEK NUMBER
DEROCERAS$WEEK <- as.numeric(strftime(DEROCERAS$date, format = '%V'))
ARYON$WEEK <- as.numeric(strftime(ARYON$DATE, format = '%V'))

# + 52  IF AFTER THE 1st OF JANUARY
for(i in (1:nrow(ARYON))){
  
  ifelse(
    
    # ARGUMENT
    ARYON$WEEK[i] < 40,
    
    # IF YES
    ARYON$WEEK[i] <- ARYON$WEEK[i] + 52,
    
    # IF NO
    ARYON$WEEK[i] <- ARYON$WEEK[i])

}

##############################################################################################################

# CREATE NEW VARIABLES
######################

# DEROCERAS / COMPUTE AGE OF THE SLUGLINGS
#-----------------------------------------

# Create an empty variable for age
DEROCERAS$age <- NA

# For loop
for(i in (1:nrow(DEROCERAS))){

  # i <- 3322

  # print(i)

  i.DEROCERAS <- DEROCERAS[i,]
  i.Slug_ID <- i.DEROCERAS$Slug_ID

  # Find hatching date
  weight.ls <- DEROCERAS[DEROCERAS$Slug_ID == i.Slug_ID,]
  i.Hatching_Date <- weight.ls[which(weight.ls$weight == 0),]

  # Add age to the slugling
  i.age <- i.DEROCERAS$date_DOY - i.Hatching_Date$date_DOY
  DEROCERAS$age[i] <- i.age

}

# Remove
rm(i, i.age, i.Slug_ID, weight.ls, i.Hatching_Date, i.DEROCERAS)

# CLEAN
DEROCERAS <- DEROCERAS[DEROCERAS$age > 0,]
DEROCERAS <- DEROCERAS[!is.na(DEROCERAS$weight),]
DEROCERAS <- DEROCERAS[DEROCERAS$age < 125,] # 2120

#-------------------------------------------------------------------------------------------------------------

# ARYON / COMPUTE AGE OF THE SLUGLINGS
#-------------------------------------

# Create an empty variable for age
ARYON$AGE <- NA

# For loop
for(i in (1:nrow(ARYON))){

  # i <- 105

  # print(i)

  i.ARYON <- ARYON[i,]
  i.Slug_ID <- i.ARYON$LABEL

  # Find hatching date
  weight.ls <- ARYON[ARYON$LABEL == i.Slug_ID,]
  
  # FIND ANY MISTAKES
  #------------------
  
  ifelse(
    
    # ARGUMENT
    "BORN" %in% weight.ls$LIFE,

  # IF YES
    { i.Hatching_Date <- weight.ls[which(weight.ls$LIFE == "BORN"),]
      i.age <- i.ARYON$DATE_DOY - i.Hatching_Date$DATE_DOY
      ARYON$AGE[i] <- i.age},

    # IF NO
    print(paste0(unique(weight.ls$LABEL), " has no birth date"))
  
  )

}

# Remove
rm(i, i.age, i.Slug_ID, weight.ls, i.Hatching_Date, i.ARYON)

##############################################################################################################

# MORTALITY RATES - DEROCERAS
#############################

# FORMAT
#-------

# SLUGLINGS AGE (WEEK)
DEROCERAS$age_week <- NA

DEROCERAS.new <- DEROCERAS[1,]

for(i in (unique(DEROCERAS$Slug_ID))){
  
  # i <- 23
  
  i.DEROCERAS <- DEROCERAS[DEROCERAS$Slug_ID == i,]
  i.DEROCERAS$age_week <- i.DEROCERAS$WEEK - min(i.DEROCERAS$WEEK)
  
  DEROCERAS.new <- rbind(DEROCERAS.new, i.DEROCERAS)

}

# CLEAN
DEROCERAS.new <- DEROCERAS.new[-1,]
DEROCERAS <- DEROCERAS.new

# EMPTY DATA FRAME
DEROCERAS.MORT <- data.frame(
  "WEEK" = 9999,
  "LIGHT_TRMT" = 9999,
  "N_WEEK_BEF" = 9999,
  "N_WEEK" = 9999,
  "MORTALITY" = 9999)

for(i in ((min(DEROCERAS$age_week) + 1):max(DEROCERAS$age_week))){
  
  # i <- 6
  
  i.DEROCERAS.MORT <- NA
  
  i.WEEK.DARK <- i
  i.WEEK.LIGHT <- i
  i.WEEK <- rbind(i.WEEK.DARK, i.WEEK.LIGHT)
  
  i.LIGHT_TRMT.DARK <- "DARK"
  i.LIGHT_TRMT.LIGHT <- "LIGHT"
  i.LIGHT_TRMT <- rbind(i.LIGHT_TRMT.DARK, i.LIGHT_TRMT.LIGHT)
  
  i.N_WEEK_BEF.DARK <- as.numeric(nrow(DEROCERAS[DEROCERAS$age_week == (i-1) & DEROCERAS$treatment == "dark",])) 
  i.N_WEEK_BEF.LIGHT <- as.numeric(nrow(DEROCERAS[DEROCERAS$age_week == (i-1) & DEROCERAS$treatment == "light",]))
  i.N_WEEK_BEF <- rbind(i.N_WEEK_BEF.DARK, i.N_WEEK_BEF.LIGHT)

  i.N_WEEK.DARK <- as.numeric(nrow(DEROCERAS[DEROCERAS$age_week == i & DEROCERAS$treatment == "dark",])) 
  i.N_WEEK.LIGHT <- as.numeric(nrow(DEROCERAS[DEROCERAS$age_week == i & DEROCERAS$treatment == "light",]))
  i.N_WEEK <- rbind(i.N_WEEK.DARK, i.N_WEEK.LIGHT)
  
  i.MORTALITY.DARK <- 100 - round(i.N_WEEK.DARK / i.N_WEEK_BEF.DARK, 3) * 100
  i.MORTALITY.LIGHT <- 100 - round(i.N_WEEK.LIGHT / i.N_WEEK_BEF.LIGHT, 3) * 100
  i.MORTALITY <- rbind(i.MORTALITY.DARK, i.MORTALITY.LIGHT)
  
  i.DEROCERAS.MORT <- as.matrix(cbind(i.WEEK, i.LIGHT_TRMT, i.N_WEEK_BEF, i.N_WEEK, i.MORTALITY))
  colnames(i.DEROCERAS.MORT) <- c("WEEK", "LIGHT_TRMT", "N_WEEK_BEF", "N_WEEK", "MORTALITY")
  
  DEROCERAS.MORT <- rbind(DEROCERAS.MORT, i.DEROCERAS.MORT)
  
}

# CLEAN
DEROCERAS.MORT <- DEROCERAS.MORT[-1,]
DEROCERAS.MORT$N_WEEK_BEF <- as.numeric(DEROCERAS.MORT$N_WEEK_BEF)
DEROCERAS.MORT$N_WEEK <- as.numeric(DEROCERAS.MORT$N_WEEK)
DEROCERAS.MORT$MORTALITY <- as.numeric(DEROCERAS.MORT$MORTALITY)
DEROCERAS.MORT$WEEK <- as.numeric(DEROCERAS.MORT$WEEK)

# REMOVE
rm(i.DEROCERAS.MORT, i.WEEK.DARK, i.WEEK.LIGHT, i.WEEK, i.LIGHT_TRMT.DARK, i.LIGHT_TRMT.LIGHT, i.LIGHT_TRMT)
rm(i.N_WEEK_BEF.DARK, i.N_WEEK_BEF.LIGHT, i.N_WEEK_BEF, i.N_WEEK.DARK, i.N_WEEK.LIGHT, i.N_WEEK)
rm(i.MORTALITY.DARK, i.MORTALITY.LIGHT, i.MORTALITY, i, i.DEROCERAS, DEROCERAS.new)

# KEPLAN-MEIER
#-------------

DEROCERAS.KM <- data.frame(
  "ID" = 9999,
  "time" = 9999,
  "status" = 9999,
  "treatment" = 9999)

for(i in (unique(DEROCERAS$Slug_ID))){
 
  # i <- 23
  
  i.DEROCERAS.KM <- DEROCERAS.KM[1,]
  
  i.DEROCERAS <- DEROCERAS[DEROCERAS$Slug_ID == i,]  

  i.DEROCERAS.KM$ID <- i
  i.DEROCERAS.KM$time <- max(i.DEROCERAS$age_week)
  ifelse(
    
    # ARGUMENT
    i.DEROCERAS.KM$time > 13,
    
    # IF YES
    i.DEROCERAS.KM$status <- 0,
      
    # IF NO
    i.DEROCERAS.KM$status <- 1)
  
  i.DEROCERAS.KM$treatment <- unique(i.DEROCERAS$treatment)
  
  DEROCERAS.KM <- rbind(DEROCERAS.KM, i.DEROCERAS.KM)

}

DEROCERAS.KM <- DEROCERAS.KM[-1,]

# ONLY KEEP SLUGLINGS THAT SURVIVED AT LEAST 2 WEEKS
DEROCERAS.KM <- DEROCERAS.KM[DEROCERAS.KM$time > 1,] # 161

rm(i.DEROCERAS, i.DEROCERAS.KM, DEROCERAS.MORT, i)

#-------------------------------------------------------------------------------------------------------------

# MORTALITY RATES - ARION
#########################

# FORMAT
#-------

# SLUGLINGS AGE (WEEK)
ARYON$AGE_WEEK <- NA

ARYON.new <- ARYON[1,]

for(i in (unique(ARYON$LABEL))){
  
  # i <- "A023"
  
  i.ARYON <- ARYON[ARYON$LABEL == i,]
  i.ARYON$AGE_WEEK <- i.ARYON$WEEK - min(i.ARYON$WEEK)
  
  ARYON.new <- rbind(ARYON.new, i.ARYON)

}

# CLEAN
ARYON.new <- ARYON.new[-1,]
ARYON <- ARYON.new

# KEPLAN-MEIER
#-------------

ARYON.KM <- data.frame(
  "ID" = 9999,
  "time" = 9999,
  "status" = 9999,
  "treatment" = 9999)

LABEL.ls <- unique(ARYON$LABEL)
LABEL.ls <- LABEL.ls[-length(LABEL.ls)]

for(i in LABEL.ls){
 
  # i <- "A023"
  
  i.ARYON.KM <- ARYON.KM[1,]
  
  i.ARYON <- ARYON[ARYON$LABEL == i,]  

  i.ARYON.KM$ID <- i
  i.ARYON.KM$time <- max(i.ARYON$AGE_WEEK)
  ifelse(
    
    # ARGUMENT
    "DEAD" %in% unique(i.ARYON$LIFE),
    
    # IF YES
    i.ARYON.KM$status <- 1,
      
    # IF NO
    i.ARYON.KM$status <- 0)
  
  i.ARYON.KM$treatment <- unique(i.ARYON$TREA)
  
  ARYON.KM <- rbind(ARYON.KM, i.ARYON.KM)

}

ARYON.KM <- ARYON.KM[-1,]

# ONLY KEEP SLUGLINGS THAT SURVIVED AT LEAST 2 WEEKS
ARYON.KM <- ARYON.KM[ARYON.KM$time > 1,] # 161

rm(i.ARYON, i.ARYON.KM, i, LABEL.ls, ARYON.new) # 188

```

# 01.1 - SLUGLINGS / GROWTH & MORTALITY CURVES

```{r 01.1 SLUGLINGS GROWTH CURVES, fig.width = 10, message = FALSE, warning = FALSE}

# 01.11 DEROCERAS - GROWTH CURVE
################################

COLOR.PALETTE <- c(wes_palettes$Rushmore1[4], wes_palettes$Rushmore1[1])
SUBSET <- DEROCERAS

# REMOVE SLUGS WITH LESS THAN 3 MEASURMENTS
KEEP.ls <- NA

for(i in unique(DEROCERAS$Slug_ID)){
  
  # i <- 164
  
  n.DEROCERAS <- nrow(SUBSET[SUBSET$Slug_ID == i,])
  
  ifelse(
    
    # ARGUMENT
    n.DEROCERAS >= 3,
    
    # IF YES
    KEEP.ls <- append(KEEP.ls, i),
    
    # IF NO
    KEEP.ls <- KEEP.ls)

}

KEEP.ls <- KEEP.ls[-1]
SUBSET <- SUBSET[SUBSET$Slug_ID %in% KEEP.ls,] # 2079

rm(n.DEROCERAS, KEEP.ls)

# MODEL DEROCERAS
#----------------
lm.DEROCERAS.exp <- lmer(log(weight) ~ age * treatment + (1|Slug_ID), data = SUBSET)

# PRINT
#------
lm.DEROCERAS.exp.tbl <- tbl_regression(lm.DEROCERAS.exp, intercept = T) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**Weight ~ Age * Treatment + (1|Slug ID)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

knit_print(lm.DEROCERAS.exp.tbl)
# print(lm.DEROCERAS.exp.tbl)

# REMOVE
rm(lm.DEROCERAS.exp.tbl)

#-------------------------------------------------------------------------------------------------------------

# VISUALIZE
#----------

# CREATE EMPTY DF
preddata <- expand.grid(
              "age" = seq(min(SUBSET$age), max(SUBSET$age, 1)), 
              "treatment" = as.factor(c("dark", "light")),
              "Slug_ID" = as.factor(unique(SUBSET$Slug_ID)))

# PREDICT
preds <- predict(lm.DEROCERAS.exp, newdata = preddata , type = "link", se.fit = TRUE)

critval <- 1.96 ## approx 95% CI
upr <- preds$fit + (critval * preds$se.fit)
lwr <- preds$fit - (critval * preds$se.fit)
fit <- preds$fit

preddata$fit <- exp(fit)
preddata$lwr <- exp(lwr)
preddata$upr <- exp(upr)

# MODEL AVERAGING
#----------------

age.ls <- unique(preddata$age)

for(i in age.ls){
  
  # i <- 84
  
  preddata.new <- preddata[1:2,]
  preddata.new[1:2,] <- NA
  
  i.preddata <- preddata[preddata$age == i,]
  
  fit.dark <- mean(i.preddata$fit[i.preddata$treatment == "dark"])
  lwr.dark <- mean(i.preddata$lwr[i.preddata$treatment == "dark"])
  upr.dark <- mean(i.preddata$upr[i.preddata$treatment == "dark"])
  
  fit.lit <- mean(i.preddata$fit[i.preddata$treatment == "light"])
  lwr.lit <- mean(i.preddata$lwr[i.preddata$treatment == "light"])
  upr.lit <- mean(i.preddata$upr[i.preddata$treatment == "light"])
  
  preddata.new$age <- c(i,i)
  preddata.new$treatment <- c("dark", "light")
  preddata.new$Slug_ID <- c("Mean", "Mean")
  preddata.new$fit <- c(fit.dark,fit.lit)
  preddata.new$lwr <- c(lwr.dark,lwr.lit)
  preddata.new$upr <- c(upr.dark,upr.lit)

  preddata <- rbind(preddata, preddata.new)
  
}

preddata <- preddata[preddata$Slug_ID == "Mean",]
preddata$age <- as.numeric(preddata$age)

# PLOT
#-----
`01.11_GROWTH.points` <- ggplot() +

  # ADD POINTS
  geom_point(
    data = SUBSET,
    aes(
      x = age,
      y = weight,
      colour = treatment,
      alpha = 0.1)) +
  
  # FIT MODELS
  geom_ribbon(
    data = preddata,
    aes(
      x = age,
      ymin = lwr,
      ymax = upr,
      fill = treatment),
    alpha = 0.3) +
  geom_line(
    data = preddata,
    aes(
      x = age,
      y = fit,
      colour = treatment,
      linetype = "bold"),
    linewidth = 2) +
  
  # ADD AESTHETICS...
  theme_minimal() +
  labs(
    x = "Sluglings age [day]",
    y = "Weight [mg]",
    colour = "Light treatment",
    title = "Deroceras reticulatum") +
  scale_colour_manual(
    values = COLOR.PALETTE,
    labels = c("DARK", "LIT")) +
  scale_fill_manual(
    values = COLOR.PALETTE) +
  guides(
    linetype = "none",
    alpha = "none",
    fill = "none",
    linewidth = "none",
    colour = "none") +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8, angle = 0, hjust = 0.5),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5))

plot(`01.11_GROWTH.points`)

# ggsave(filename = "01.11_GROWTH.points.jpeg",
#        plot = `01.11_GROWTH.points`, path = HOME,
#        height = 8, width = 16, units = "cm")

# REMOVE
rm(fit, lm.DEROCERAS.exp)
rm(i.preddata, preddata, preddata.new, preds, age.ls, critval, fit.dark, fit.lit, i, lwr, lwr.dark)
rm(lwr.lit, upr, upr.dark, upr.lit)

#-------------------------------------------------------------------------------------------------------------

# 01.12 DEROCERAS - SURVIVAL ANALYSIS
#####################################

# PLOT
`01.12_MORTALITY` <- survfit2(
  Surv(time, status) ~ treatment,
  data = DEROCERAS.KM) |>
  ggsurvfit(
    linewidth = 1) +
  add_confidence_interval() +
  
  # ADD AESTHETICS...
  theme_minimal() +
  labs(
    x = "Sluglings age [week]",
    y = "Survival probability",
    colour = "Light treatment",
    title = "Deroceras reticulatum") +
  scale_colour_manual(
    values = COLOR.PALETTE,
    labels = c("DARK", "LIT")) +
  scale_fill_manual(
    values = COLOR.PALETTE) +
  coord_cartesian(
    xlim = c(2, 15)) +
  guides(
    fill = "none") +
  theme(
    legend.position = c(0.8, 0.85),
    legend.title = element_text(size = 8, face = "bold"),
    legend.text = element_text(size = 8, face = "bold"),
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8, angle = 0, hjust = 0.5),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5))

plot(`01.12_MORTALITY`)

# TEST
#-----
COX.DEROCERAS <- coxph(Surv(time, status) ~ treatment, data = DEROCERAS.KM)
COX.DEROCERAS.tbl <- tbl_regression(COX.DEROCERAS, exp = TRUE) %>%

  modify_spanning_header(
    c(estimate, ci, p.value) ~ "**Deroceras reticulatum**") %>%

  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()
  
knit_print(COX.DEROCERAS.tbl)
# print(COX.DEROCERAS.tbl)

rm(SUBSET, COX.DEROCERAS, COX.DEROCERAS.tbl)
rm(DEROCERAS, DEROCERAS.KM)

##############################################################################################################

# 01.13 ARYON - PLOT EXPONENTIAL CURVE
######################################

# SUBSET
#-------
# REMOVE ZEROES
SUBSET <- ARYON[ARYON$LIFE == "ALIVE",]
SUBSET <- SUBSET[SUBSET$AGE > 0,]
SUBSET <- SUBSET[! is.na(SUBSET$AGE),]

# REMOVE SLUGS WITH LESS THAN 3 MEASURMENTS
KEEP.ls <- NA

for(i in unique(SUBSET$LABEL)){
  
  # i <- 123
  
  n.ARION <- nrow(SUBSET[SUBSET$LABEL == i,])
  
  ifelse(
    
    # ARGUMENT
    n.ARION >= 3,
    
    # IF YES
    KEEP.ls <- append(KEEP.ls, i),
    
    # IF NO
    KEEP.ls <- KEEP.ls)

}

KEEP.ls <- KEEP.ls[-1]
SUBSET <- SUBSET[SUBSET$LABEL %in% KEEP.ls,]

rm(n.ARION, KEEP.ls)

# MODEL ARION
#------------
lm.ARION.exp <- lmer(log(WEIGHT) ~ AGE * TREA + (1|LABEL), data = SUBSET)

# Print
#------
lm.ARION.exp.tbl <- tbl_regression(lm.ARION.exp, intercept = T) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**N moves ~ Lux * Time + (1|Week)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

knit_print(lm.ARION.exp.tbl)
# print(lm.ARION.exp.tbl)

# SAVE
# gtsave(as_gt(lm.ARION.exp.tbl),
#        file = file.path(paste0(HOME,"/lm.ARION.exp.tbl")))

# REMOVE
rm(lm.ARION.exp.tbl)

#-------------------------------------------------------------------------------------------------------------

# VISUALIZE
#----------

# CREATE EMPTY DF
preddata <- expand.grid(
              "AGE" = seq(min(SUBSET$AGE), max(SUBSET$AGE, 1)), 
              "TREA" = as.factor(c("DARK", "LIGHT")),
              "LABEL" = as.factor(unique(SUBSET$LABEL)))

# PREDICT
preds <- predict(lm.ARION.exp, newdata = preddata , type = "link", se.fit = TRUE)

critval <- 1.96 ## approx 95% CI
upr <- preds$fit + (critval * preds$se.fit)
lwr <- preds$fit - (critval * preds$se.fit)
fit <- preds$fit

preddata$fit <- exp(fit)
preddata$lwr <- exp(lwr)
preddata$upr <- exp(upr)

# MODEL AVERAGING
#----------------

AGE.ls <- unique(preddata$AGE)

for(i in AGE.ls){
  
  # i <- 84
  
  preddata.new <- preddata[1:2,]
  preddata.new[1:2,] <- NA
  
  i.preddata <- preddata[preddata$AGE == i,]
  
  fit.dark <- mean(i.preddata$fit[i.preddata$TREA == "DARK"])
  lwr.dark <- mean(i.preddata$lwr[i.preddata$TREA == "DARK"])
  upr.dark <- mean(i.preddata$upr[i.preddata$TREA == "DARK"])
  
  fit.lit <- mean(i.preddata$fit[i.preddata$TREA == "LIGHT"])
  lwr.lit <- mean(i.preddata$lwr[i.preddata$TREA == "LIGHT"])
  upr.lit <- mean(i.preddata$upr[i.preddata$TREA == "LIGHT"])
  
  preddata.new$AGE <- c(i,i)
  preddata.new$TREA <- c("DARK", "LIGHT")
  preddata.new$LABEL <- c("Mean", "Mean")
  preddata.new$fit <- c(fit.dark,fit.lit)
  preddata.new$lwr <- c(lwr.dark,lwr.lit)
  preddata.new$upr <- c(upr.dark,upr.lit)

  preddata <- rbind(preddata, preddata.new)
  
}

preddata <- preddata[preddata$LABEL == "Mean",]
preddata$AGE <- as.numeric(preddata$AGE)

# PLOT
`01.13_GROWTH.points` <- ggplot() +

  # ADD POINTS
  geom_point(
    data = SUBSET,
    aes(
      x = AGE,
      y = WEIGHT,
      colour = TREA,
      alpha = 0.1)) +
  
  # FIT MODELS
  geom_ribbon(
    data = preddata,
    aes(
      x = AGE,
      ymin = lwr,
      ymax = upr,
      fill = TREA),
    alpha = 0.32) +
  geom_line(
    data = preddata,
    aes(
      x = AGE,
      y = fit,
      colour = TREA,
      linetype = "bold"),
      linewidth = 2) +
  
  # ADD AESTHETICS...
  theme_minimal() +
  labs(
    x = "Sluglings age [day]",
    y = "Weight [mg]",
    colour = "Light treatment",
    title = "Arion lusitanicus") +
  scale_colour_manual(
    values = COLOR.PALETTE,
    labels = c("DARK", "LIT")) +
  scale_fill_manual(
    values = COLOR.PALETTE) +
  guides(
    linetype = "none",
    alpha = "none",
    fill = "none",
    linewidth = "none",
    colour = "none") +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 10, face = "bold"),
    axis.text.x = element_text(size = 8, angle = 0, hjust = 0.5),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5))

plot(`01.13_GROWTH.points`)

# REMOVE
rm(fit, lm.ARION.exp, AGE.ls)
rm(i.preddata, preddata, preddata.new, preds, critval, fit.dark, fit.lit, i, lwr, lwr.dark)
rm(lwr.lit, upr, upr.dark, upr.lit)

#-------------------------------------------------------------------------------------------------------------

# 01.14 ARION - SURVIVAL ANALYSIS
#################################

# PLOT
`01.14_MORTALITY` <- survfit2(
  Surv(time, status) ~ treatment,
  data = ARYON.KM) |>
  ggsurvfit(
    linewidth = 1) +
  add_confidence_interval() +

  # ADD AESTHETICS...
  theme_minimal() +
  labs(
    x = "Sluglings age [week]",
    y = "Survival probability",
    colour = "Light treatment",
    title = "Arion lusitanicus") +
  scale_colour_manual(
    values = COLOR.PALETTE,
    labels = c("DARK", "LIT")) +
  scale_fill_manual(
    values = COLOR.PALETTE) +
  coord_cartesian(xlim = c(3, 17)) +
  guides(
    fill = "none",
    colour = "none") +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 10, face = "bold"),
    axis.text.x = element_text(size = 8, angle = 0, hjust = 0.5),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5))

plot(`01.14_MORTALITY`)

# TEST
#-----

COX.ARYON <- coxph(Surv(time, status) ~ treatment, data = ARYON.KM)
COX.ARYON.tbl <- tbl_regression(COX.ARYON, exp = TRUE) %>%

  modify_spanning_header(
    c(estimate, ci, p.value) ~ "**Arion reticulatum**") %>%

  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()
  
knit_print(COX.ARYON.tbl)
# print(COX.ARYON.tbl)

rm(SUBSET, COX.ARYON, COX.ARYON.tbl)
rm(ARYON, ARYON.KM)

# FINAL PLOT
#-----------

`01.1_SLUGLINGS` <- grid.arrange(
`01.11_GROWTH.points`,
`01.12_MORTALITY`,
`01.13_GROWTH.points`,
`01.14_MORTALITY`)


rm(`01.1_SLUGLINGS`, `01.11_GROWTH.points`, `01.12_MORTALITY`,`01.13_GROWTH.points`, `01.14_MORTALITY`)

```

# 01.2 - SLUGLINGS / BEHAVIOUR

```{r 01.2 SLUGLINGS BEHAVIOUR NEW, fig.width = 10, message = FALSE, warning = FALSE}

COLOR.PALETTE <- c(wes_palettes$Rushmore1[4], wes_palettes$Rushmore1[1])

# 01.2 FORMAT
#############

# TIME
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^0:", "00:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^1:", "01:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^2:", "02:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^3:", "03:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^4:", "04:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^5:", "05:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^6:", "06:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^7:", "07:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^8:", "08:")
SHIFT.TABLE$TIME <- str_replace_all(SHIFT.TABLE$TIME, "^9:", "09:")

SHIFT.TABLE$ID <- paste0(SHIFT.TABLE$DATE, "-", SHIFT.TABLE$TIME, "-", SHIFT.TABLE$LIGHT.TREA)

# CLEAN DATA (WHEN THEY ARE MORE THAN 20 ARROWS, IT'S A MISTAKE)
#---------------------------------------------------------------

# List of ID's
ID.ls <- unique(SHIFT.TABLE$ID)

# Create an empty data table
SHIFT.TABLE.new <- SHIFT.TABLE
SHIFT.TABLE.new <- SHIFT.TABLE.new[1,]
SHIFT.TABLE.new <- SHIFT.TABLE.new[NA,]

# Fill with new rows (should not exceed the number of slugs)
for(i in ID.ls){
  
  # i <- "2024:01:25-22:45-DARK"
  
  i.SHIFT.TABLE <- SHIFT.TABLE[SHIFT.TABLE$ID == i,]
  i.n.slugs <- unique(i.SHIFT.TABLE$N_SLUGS)

  ifelse(
    
    # ARGUMENT
    nrow(i.SHIFT.TABLE) < i.n.slugs,
    
    # IF YES
    SHIFT.TABLE.new <- rbind(SHIFT.TABLE.new, i.SHIFT.TABLE),
    
    # IF NO
    SHIFT.TABLE.new <- SHIFT.TABLE.new)
  
}

SHIFT.TABLE <- SHIFT.TABLE.new

# REMOVE FIRST LINE FULL OF NA's
SHIFT.TABLE <- SHIFT.TABLE[-1,]

# TIME AS NUMERIC
#----------------
SHIFT.TABLE$TIME.num <- SHIFT.TABLE$TIME
SHIFT.TABLE$TIME.num <- str_replace_all(SHIFT.TABLE$TIME.num, ":00", ".0")
SHIFT.TABLE$TIME.num <- str_replace_all(SHIFT.TABLE$TIME.num, ":15", ".25")
SHIFT.TABLE$TIME.num <- str_replace_all(SHIFT.TABLE$TIME.num, ":30", ".5")
SHIFT.TABLE$TIME.num <- str_replace_all(SHIFT.TABLE$TIME.num, ":45", ".75")
SHIFT.TABLE$TIME.num <- as.numeric(SHIFT.TABLE$TIME.num)

# DATE TIME
SHIFT.TABLE$TIME.DATE <- paste(SHIFT.TABLE$DATE, SHIFT.TABLE$TIME)

# REMOVE
rm(i.SHIFT.TABLE, SHIFT.TABLE.new, i, ID.ls)

#-------------------------------------------------------------------------------------------------------------

# REFORMAT (N MOVES PER TIME UNIT)
#---------------------------------

# CREATE AN EMPTY TABLE
WEEK.ls <- unique(SHIFT.TABLE$WEEK)
TIME.ls <- unique(SHIFT.TABLE$TIME)

TIME.DATE <- expand.grid("DATE" = unique(SHIFT.TABLE$DATE),"TIME" = TIME.ls)
TIME.DATE.ls <- paste(TIME.DATE$DATE, TIME.DATE$TIME)

MOVE.TABLE <- expand.grid("LIGHT.TREA" = unique(SHIFT.TABLE$LIGHT.TREA), "TIME.DATE" = TIME.DATE.ls, "WEEK" = WEEK.ls)

MOVE.TABLE$N.MOVES.row <- NA
MOVE.TABLE$N.MOVES.avg <- NA
MOVE.TABLE$TIME <- NA

# FILL FOR LOOP
for(i in (1:nrow(MOVE.TABLE))){
  
  # i <- 895 
  
  i.LIGHT.TREA <- MOVE.TABLE$LIGHT.TREA[i]
  i.TIME.DATE <- MOVE.TABLE$TIME.DATE[i]
  i.WEEK <- MOVE.TABLE$WEEK[i]
  
  # MOVE TABLE
  i.MOVE.TABLE <- SHIFT.TABLE[SHIFT.TABLE$LIGHT.TREA == i.LIGHT.TREA & 
                              SHIFT.TABLE$TIME.DATE == i.TIME.DATE & 
                              SHIFT.TABLE$WEEK == i.WEEK,]

  # N MOVES
  i.n.slug <- unique(SHIFT.TABLE$N_SLUGS[SHIFT.TABLE$WEEK == i.WEEK & SHIFT.TABLE$LIGHT.TREA == i.LIGHT.TREA])
  MOVE.TABLE$N.MOVES.row[i] <- nrow(i.MOVE.TABLE)
  
  ifelse(

    # ARGUMENT
    MOVE.TABLE$N.MOVES.row[i] == 0,
    
    # IF YES
    MOVE.TABLE$N.MOVES.avg[i] <- 0,
    
    # IF NO
    MOVE.TABLE$N.MOVES.avg[i] <-  MOVE.TABLE$N.MOVES.row[i] / i.n.slug)
  
  MOVE.TABLE$TIME[i] <- i.TIME.DATE <- substr(i.TIME.DATE, 12, 16)

}

# REMOVE FIRST LINE FULL OF NA's
MOVE.TABLE <- MOVE.TABLE[-1,]

# TIME AS NUMERIC
#----------------
MOVE.TABLE$TIME.num <- MOVE.TABLE$TIME

MOVE.TABLE$TIME.num <- str_replace_all(MOVE.TABLE$TIME.num, ":00", ".0")
MOVE.TABLE$TIME.num <- str_replace_all(MOVE.TABLE$TIME.num, ":15", ".25")
MOVE.TABLE$TIME.num <- str_replace_all(MOVE.TABLE$TIME.num, ":30", ".5")
MOVE.TABLE$TIME.num <- str_replace_all(MOVE.TABLE$TIME.num, ":45", ".75")

MOVE.TABLE$TIME.num <- as.numeric(MOVE.TABLE$TIME.num)

# REMOVE
rm(i.MOVE.TABLE, i, i.LIGHT.TREA, i.n.slug, i.TIME.DATE, i.WEEK, TIME.DATE.ls, TIME.ls, WEEK.ls)

##############################################################################################################

# MODELS
#-------
MOVE.TABLE$TIME.radian <- MOVE.TABLE$TIME.num / 24 * 2 * pi

# FULL MODEL
lm.model.radian <- lmer(N.MOVES.row ~ sin(TIME.radian) * LIGHT.TREA + 
                                          cos(TIME.radian) * LIGHT.TREA + 
                                          sin(2 * TIME.radian) * LIGHT.TREA +
                                          cos(2 * TIME.radian) * LIGHT.TREA +
                                          (1|WEEK), data = MOVE.TABLE) 
  
qqnorm(resid(lm.model.radian))
qqline(resid(lm.model.radian))

# WRITE
lm.model.radian.tbl <- tbl_regression(lm.model.radian, 
                                      intercept = T,
                                      pvalue_fun = ~ style_pvalue(.x, digits = 3),
                                      estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**N moves ~ Lux * Time + (1|Week)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(lm.model.radian.tbl)
# print(lm.model.radian.tbl)

rm(lm.model.radian.tbl)

#-------------------------------------------------------------------------------------------------------------

# SIMULATE DATA
#--------------

# Create empty df
preddata <- expand.grid(
            "TIME.radian" = seq(min(MOVE.TABLE$TIME.radian), max(MOVE.TABLE$TIME.radian), length = 100), 
            "LIGHT.TREA" = as.factor(c("DARK", "LIT")),
            "WEEK" = as.factor(seq(2, 6)))

# round
preddata$TIME.radian <- round(preddata$TIME.radian, 4)

# PREDICT
preds <- predict(lm.model.radian, newdata = preddata , type = "link", se.fit = TRUE)

critval <- 1.96 ## approx 95% CI
upr <- preds$fit + (critval * preds$se.fit)
lwr <- preds$fit - (critval * preds$se.fit)
fit <- preds$fit

preddata$fit <- fit
preddata$lwr <- lwr
preddata$upr <- upr

# MODEL AVERAGING
#----------------
radian.ls <- unique(preddata$TIME.radian)

for(i in radian.ls){
  
  # i <- 0.9421
  
  preddata.new <- preddata[1:2,]
  preddata.new[1:2,] <- NA
  
  i.preddata <- preddata[preddata$TIME.radian == i,]
  
  fit.dark <- mean(i.preddata$fit[i.preddata$LIGHT.TREA == "DARK"])
  lwr.dark <- mean(i.preddata$lwr[i.preddata$LIGHT.TREA == "DARK"])
  upr.dark <- mean(i.preddata$upr[i.preddata$LIGHT.TREA == "DARK"])
  
  fit.lit <- mean(i.preddata$fit[i.preddata$LIGHT.TREA == "LIT"])
  lwr.lit <- mean(i.preddata$lwr[i.preddata$LIGHT.TREA == "LIT"])
  upr.lit <- mean(i.preddata$upr[i.preddata$LIGHT.TREA == "LIT"])
  
  preddata.new$TIME.radian <- c(i,i)
  preddata.new$LIGHT.TREA <- c("DARK", "LIT")
  preddata.new$WEEK <- c("Mean", "Mean")
  preddata.new$fit <- c(fit.dark,fit.lit)
  preddata.new$lwr <- c(lwr.dark,lwr.lit)
  preddata.new$upr <- c(upr.dark,upr.lit)

  preddata <- rbind(preddata, preddata.new)
  
}

preddata <- preddata[preddata$WEEK == "Mean",]

# PLOT
#-----
PLOT.01.06.N <- ggplot() +
  
# ADD POLYGONS FOR NIGHT
geom_rect(
  aes(
    xmin = -Inf,
    xmax = 7 / 24 * 2 * pi,
    ymin = -Inf,
    ymax = Inf),
  alpha = 0.6,
  fill = "grey10") +

geom_rect(
aes(
  xmin = 17 / 24 * 2 * pi,
  xmax = Inf,
  ymin = -Inf,
  ymax = Inf),
alpha = 0.6,
fill = "grey10") +

# ADD POINTS
geom_point(
  data = MOVE.TABLE,
  aes(
    x = TIME.radian,
    y = N.MOVES.avg,
    colour = LIGHT.TREA), 
  alpha = 0.2) +

# FIT CI
geom_ribbon(
  data = preddata,
  aes(
    x = TIME.radian,
    ymin = lwr,
    ymax = upr,
    fill = LIGHT.TREA),
  alpha = 0.5) +

# FIT MODEL
geom_line(
  data = preddata,
  aes(
    x = TIME.radian,
    y = fit,
    colour = LIGHT.TREA,
    linetype = "bold"),
  linewidth = 2) +

# ADD AESTHETICS...
theme_minimal() +
labs(x = "Time",
     y = "Proportion of slugs moving",
     colour = "Light treatment") +

scale_colour_manual(values = COLOR.PALETTE) +
scale_fill_manual(values = COLOR.PALETTE) +
scale_x_continuous(
  breaks = c(0 / 24 * 2 * pi, 6 / 24 * 2 * pi, 12 / 24 * 2 * pi, 18 / 24 * 2 * pi, 24 / 24 * 2 * pi),
  label = c("00h00","06h00", "12h00", "18h00", "24h00")) +
guides(linetype = "none",
       alpha = "none",
       fill = "none",
       size = "none") +
theme(
  legend.position = c(0.8, 0.85),
  legend.title = element_text(size = 16, face = "bold"),
  legend.text = element_text(size = 16, face = "bold"),
  axis.title.x = element_text(size = 20, face = "bold"),
  axis.text.x = element_text(size = 12, angle = 0, hjust = 0.5),
  axis.title.y = element_text(size = 20, face = "bold"),
  axis.text.y = element_text(size = 12, angle = 0, hjust = 0.5))

plot(PLOT.01.06.N)

rm(PLOT.01.06.N, preddata, preds, fit, lwr, upr, critval, lm.model.radian, preddata.new)
rm(i, fit.dark, fit.lit, lwr.dark, lwr.lit, upr.dark, upr.lit, radian.ls)
rm(i.preddata, i.preddata.new)

##############################################################################################################

# FINAL REMOVE
#-------------
rm(MOVE.TABLE, SHIFT.TABLE)

```

# 02.0 - TRACKPLATES / DATA FORMATING & EXPLORATORY PLOTS

```{r 02.0 TRACKPLATES DATA FORMATING & EXPLORATORY PLOTS, fig.width = 10, warning = FALSE, message = FALSE}

# FORMAT TRACKPLATES
#-------------------

TRACKPLATES <- data.frame(
  "YEAR" = 9999,
  "DATE" = 9999,
  "HABITAT" = 9999,
  "STUDY.SITE" = 9999,
  "LIGHT_TRMT" = 9999,
  "PLATE_ID" = 9999,
  "PLATE_LOC" = 9999,
  "MICE_TRACKS_N" = 9999,
  "SLUG_TRACKS_PROP" = 9999)

# 2022
#-----
for(i in (1:nrow(TRACKS.22))){
  
  # i <- 124
  
  i.TRACKPLATES <- TRACKPLATES[1,]
  
  i.TRACKPLATES$YEAR <- "2022"
  i.TRACKPLATES$DATE <- TRACKS.22$Datetime.laid[i]
  i.TRACKPLATES$HABITAT <- "WFS"
  i.TRACKPLATES$STUDY.SITE <- TRACKS.22$STUDY_SITE[i] 
  i.TRACKPLATES$LIGHT_TRMT <- TRACKS.22$LIGHT_TRMT[i]
  i.TRACKPLATES$PLATE_ID <- TRACKS.22$PLATE_ID[i]
  i.TRACKPLATES$PLATE_LOC <- TRACKS.22$PLATE_LOC[i]
  i.TRACKPLATES$MICE_TRACKS_N <- TRACKS.22$MICE_TRACKS_N[i]
  i.TRACKPLATES$SLUG_TRACKS_PROP <- TRACKS.22$SLUG_TRACKS_PROP[i]
  
  TRACKPLATES <- rbind(TRACKPLATES, i.TRACKPLATES)
  
}

# 2023
#-----
for(i in (1:nrow(TRACKS.23))){
  
  # i <- 124
  
  i.TRACKPLATES <- TRACKPLATES[1,]
  
  i.TRACKPLATES$YEAR <- "2023"
  i.TRACKPLATES$DATE <- TRACKS.23$data1[i]
  ifelse(TRACKS.23$site_type[i] == "Fallow", i.TRACKPLATES$HABITAT <- "WFS",  i.TRACKPLATES$HABITAT <- "GRASSLAND")
  i.TRACKPLATES$STUDY.SITE <- TRACKS.23$site_id[i] 
  ifelse(TRACKS.23$treatment[i] == "Dark", i.TRACKPLATES$LIGHT_TRMT <- "DARK",  i.TRACKPLATES$LIGHT_TRMT <- "LIGHT")
  i.TRACKPLATES$PLATE_ID <- TRACKS.23$plate_nb[i]
  ifelse(TRACKS.23$plate_position[i] == "D", i.TRACKPLATES$PLATE_LOC <- "CLOSE",  i.TRACKPLATES$PLATE_LOC <- "FAR")
  i.TRACKPLATES$MICE_TRACKS_N <- TRACKS.23$tracks_number[i]
  i.TRACKPLATES$SLUG_TRACKS_PROP <- TRACKS.23$Slug[i]
  
  TRACKPLATES <- rbind(TRACKPLATES, i.TRACKPLATES)
  
}

rm(TRACKS.22, TRACKS.23, i.TRACKPLATES)

# RENAME STUDY SITES
#-------------------
TRACKPLATES$STUDY.SITE <- str_replace(TRACKPLATES$STUDY.SITE, "\\b1\\b", "YELLOWHAMMER")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b2\\b", "WOODPECKER")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b3\\b", "CHAMOIS")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b4\\b", "DEER")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b5\\b", "QUAIL")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b6\\b", "UPUPA")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b7\\b", "BADGER")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b8\\b", "HORNET")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "\\b9\\b", "ANTS")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "10", "MARTEN")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "11", "GRASS SNAKE")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "12", "LIZARD")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "25", "TOAD")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "26", "PEREGRINE")
TRACKPLATES$STUDY.SITE <- str_replace_all(TRACKPLATES$STUDY.SITE, "27", "EAGLE")

# CLEAN
#------
TRACKPLATES <- TRACKPLATES[-1,]
TRACKPLATES$DATE <- as.Date(TRACKPLATES$DATE, format = "%d-%m-%y")
TRACKPLATES$MICE_TRACKS_N <- as.numeric(TRACKPLATES$MICE_TRACKS_N)
TRACKPLATES <- TRACKPLATES[!is.na(TRACKPLATES$DATE),]

# CREATE NEW VARIABLE
#####################

# DOY
TRACKPLATES$DATE_DOY <- yday(TRACKPLATES$DATE)

# TREATMENT
TRACKPLATES$TREATMENT <- paste0(TRACKPLATES$LIGHT_TRMT, "-", TRACKPLATES$PLATE_LOC)

# BINOMIAL
TRACKPLATES$SLUG_TRACKS_BIN <- NA
for(i in (1:nrow(TRACKPLATES))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    TRACKPLATES$SLUG_TRACKS_PROP[i] > 0,
    
    # IF YES
    TRACKPLATES$SLUG_TRACKS_BIN[i] <- 1,
    
    # IF NO
    TRACKPLATES$SLUG_TRACKS_BIN[i] <- 0)

}

# MERGE PROP 2022 (0 - 1) & 2023 (0 - 100)
#-----------------------------------------

for(i in (1:nrow(TRACKPLATES))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    TRACKPLATES$SLUG_TRACKS_PROP[i] < 1,
    
    # IF YES
    TRACKPLATES$SLUG_TRACKS_PROP[i] <- TRACKPLATES$SLUG_TRACKS_PROP[i] * 100,
    
    # IF NO
    TRACKPLATES$SLUG_TRACKS_PROP[i] <- TRACKPLATES$SLUG_TRACKS_PROP[i])

}

rm(i)

#-------------------------------------------------------------------------------------------------------------

# ADD ABIOTIC
#############

# SAMP ID (+1 because recovered the day after!)
#----------------------------------------------
TRACKPLATES$SAMP_ID <- format(TRACKPLATES$DATE  + 1, format = "%y%m%d")
TRACKPLATES$SAMP_ID <- as.character(TRACKPLATES$SAMP_ID)

# TEMP & RAIN
#------------

TRACKPLATES$RAIN <- NA
TRACKPLATES$TEMP <- NA

for(i in (1:nrow(TRACKPLATES))){
  
  # i <- 43
  
  i.SAMP_ID <- TRACKPLATES$SAMP_ID[i]
  i.ABIOTIC <- ABIOTIC[ABIOTIC$DATE == i.SAMP_ID,]
  
  TRACKPLATES$RAIN[i] <- i.ABIOTIC$RAIN_SUM12H[i.ABIOTIC$TIME == "08h00"] 
  TRACKPLATES$TEMP[i] <- i.ABIOTIC$TEMP_12H[i.ABIOTIC$TIME == "08h00"]
  
}

rm(i, i.SAMP_ID, i.ABIOTIC)

##############################################################################################################

# 02.01 EXPLORATORY PLOTS / N PLATES LAID
#########################################

# HABITAT
COLOR.PALETTE <- c(wes_palettes$Cavalcanti1[2], "white")

# SAMPLE SIZE
#------------

# HABITAT
`02.01_TRACKPLATES.HABITAT` <- ggplot(
  data = TRACKPLATES, 
  aes(x = YEAR,
      fill = HABITAT,
      pattern = LIGHT_TRMT)) +
  geom_bar_pattern(
    color = "black",
    position = position_dodge(preserve = "single"),
    pattern_fill = "burlywood",
    pattern_color = "burlywood",
    pattern_angle = 45, 
    pattern_density = 0.25,
    pattern_spacing = 0.025, 
    pattern_key_scale_factor = 0.6) +  
  labs(
    x = "Year",
    y = "n trackplates") +
  scale_fill_manual(
    values = COLOR.PALETTE,
    guide = guide_legend(
    override.aes = list(pattern = "none"))) +
  theme_minimal() +
  scale_pattern_manual(values = c(DARK   = "none", LIGHT  = "stripe")) +
  theme(
    # legend.position = c(0.1, 0.8),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12, angle = 0, hjust = 1),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`02.01_TRACKPLATES.HABITAT`)

# SAVE
# ggsave(filename = paste0("02.01_TRACKPLATES.HABITAT.jpeg"),
#          plot = `02.01_TRACKPLATES.HABITAT`, path = HOME,
#          height = 12, width = 16, units = "cm")

# STUDY SITE
`02.02_TRACKPLATES.SITE` <- ggplot(
  data = TRACKPLATES, 
  aes(x = STUDY.SITE,
      fill = HABITAT,
      pattern = LIGHT_TRMT)) +
  geom_bar_pattern(
    color = "black",
    position = position_dodge(preserve = "single"),
    pattern_fill = "burlywood",
    pattern_color = "burlywood",
    pattern_angle = 45, 
    pattern_density = 0.25,
    pattern_spacing = 0.025, 
    pattern_key_scale_factor = 0.6) +  
  labs(
    x = "Study site",
    y = "n trackplates") +
  scale_fill_manual(
    values = COLOR.PALETTE,
    guide = guide_legend(
    override.aes = list(pattern = "none"))) +
  theme_minimal() +
  scale_pattern_manual(values = c(DARK   = "none", LIGHT  = "stripe")) +
  theme(
    # legend.position = c(0.1, 0.8),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`02.02_TRACKPLATES.SITE`)

# SAVE
# ggsave(filename = paste0("02.02_TRACKPLATES.SITE.jpeg"),
#          plot = `02.02_TRACKPLATES.SITE`, path = HOME,
#          height = 12, width = 16, units = "cm")

rm(`02.01_TRACKPLATES.HABITAT`, `02.02_TRACKPLATES.SITE`, COLOR.PALETTE)

##############################################################################################################

# 02.02 PROPORTION OF TRACKS - ONLY ILLUMINATED BUT FAR <vs> CLOSE
##################################################################

COLOR.PALETTE <- c(wes_palettes$Cavalcanti1[2], "white")
SUBSET <- TRACKPLATES[TRACKPLATES$LIGHT_TRMT == "LIGHT",] # 737

# 02.02 - PIE CHART HABITAT & LIGHT TREATMENT - PROPORTION
#---------------------------------------------------------

columns = c("HABITAT","TREATMENT","PRESENCE", "N", "PERCENTAGE") 
PIE = data.frame(matrix(nrow = 8, ncol = length(columns))) 
colnames(PIE) = columns

PIE$HABITAT <- c("WFS", "WFS", "WFS", "WFS", "GRASSLAND", "GRASSLAND",  "GRASSLAND",  "GRASSLAND")
PIE$TREATMENT <- c("DARK", "DARK", "LIGHT", "LIGHT", "DARK", "DARK", "LIGHT", "LIGHT") 
PIE$PRESENCE <- c("YES", "NO", "YES", "NO", "YES", "NO", "YES", "NO")
PIE$N <- c(
          nrow(SUBSET[SUBSET$HABITAT == "WFS" & SUBSET$PLATE_LOC == "FAR" & SUBSET$SLUG_TRACKS_BIN == 1,]),
          nrow(SUBSET[SUBSET$HABITAT == "WFS" & SUBSET$PLATE_LOC == "FAR" & SUBSET$SLUG_TRACKS_BIN == 0,]),
          nrow(SUBSET[SUBSET$HABITAT == "WFS" & SUBSET$PLATE_LOC == "CLOSE" & SUBSET$SLUG_TRACKS_BIN == 1,]),
          nrow(SUBSET[SUBSET$HABITAT == "WFS" & SUBSET$PLATE_LOC == "CLOSE" & SUBSET$SLUG_TRACKS_BIN == 0,]),
          nrow(SUBSET[SUBSET$HABITAT == "GRASSLAND" & SUBSET$PLATE_LOC == "FAR" & SUBSET$SLUG_TRACKS_BIN == 1,]),
          nrow(SUBSET[SUBSET$HABITAT == "GRASSLAND" & SUBSET$PLATE_LOC == "FAR" & SUBSET$SLUG_TRACKS_BIN == 0,]),
          nrow(SUBSET[SUBSET$HABITAT == "GRASSLAND" & SUBSET$PLATE_LOC == "CLOSE" & SUBSET$SLUG_TRACKS_BIN == 1,]),
          nrow(SUBSET[SUBSET$HABITAT == "GRASSLAND" & SUBSET$PLATE_LOC == "CLOSE" & SUBSET$SLUG_TRACKS_BIN == 0,]))
PIE$PERCENTAGE <- c(
          round(PIE$N[1] / (PIE$N[1] + PIE$N[2]), 2),
          round(PIE$N[2] / (PIE$N[1] + PIE$N[2]), 2),
          round(PIE$N[3] / (PIE$N[3] + PIE$N[4]), 2),
          round(PIE$N[4] / (PIE$N[3] + PIE$N[4]), 2),
          round(PIE$N[5] / (PIE$N[5] + PIE$N[6]), 2),
          round(PIE$N[6] / (PIE$N[5] + PIE$N[6]), 2),
          round(PIE$N[7] / (PIE$N[7] + PIE$N[8]), 2),
          round(PIE$N[8] / (PIE$N[7] + PIE$N[8]), 2))

PIE$PERCENTAGE <- paste0((PIE$PERCENTAGE * 100), "%")
rm(columns)

# GRASSLAND
`02.02_TRACKPLATES.HABITAT.GRASSLAND.pie` <- ggplot(
  data = PIE[PIE$HABITAT == "GRASSLAND",],
  aes(
    x = "",
    y = N,
    fill = PRESENCE,
    pattern = TREATMENT)) +
  geom_col_pattern(
    color = "black",
    pattern_color = "burlywood",
    pattern_fill = "burlywood",
    pattern_angle = 45,
    pattern_density = 0.25,
    pattern_spacing = 0.05,
    pattern_key_scale_factor = 0.6) +
  coord_polar(theta = "y", start = 0) +
  geom_label(aes(label = PERCENTAGE),
             color = "white",
             size = 4,
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  scale_fill_manual(values = c("grey75", wes_palettes$Cavalcanti1[2])) +
  scale_pattern_manual(
    values = c("LIGHT" = "stripe", "DARK"  = "none"),
    name = "Treatment",
    labels = c("DARK", "LIGHT")) + 
  theme_minimal() +
  guides(pattern = "none") +
  facet_wrap(factor(TREATMENT, levels = c('LIGHT', 'DARK')) ~ ., dir = "h") +
  theme(
    legend.position = "top",
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    strip.text.x = element_blank())

# WFS
`02.02_TRACKPLATES.HABITAT.WFS.pie` <- ggplot(
  data = PIE[PIE$HABITAT == "WFS",],
  aes(
    x = "",
    y = N,
    fill = PRESENCE,
    pattern = TREATMENT)) +
  geom_col_pattern(
    color = "black",
    pattern_color = "burlywood",
    pattern_fill = "burlywood",
    pattern_angle = 45,
    pattern_density = 0.25,
    pattern_spacing = 0.05,
    pattern_key_scale_factor = 0.6) +
  coord_polar(theta = "y", start = 0) +
  geom_label(aes(label = PERCENTAGE),
             size = 4,
             color = "black",
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  scale_fill_manual(values = c("grey75", "white")) +
  scale_pattern_manual(
    values = c("LIGHT" = "stripe", "DARK"  = "none"),
    name = "Treatment",
    labels = c("DARK", "LIGHT")) + 
  theme_minimal() +
  guides(pattern = "none") +
  facet_wrap(factor(TREATMENT, levels = c('LIGHT', 'DARK')) ~ ., dir = "h") +
  theme(
    legend.position = "top",
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    strip.text.x = element_blank())

# MERGE
`02.02_TRACKPLATES.HABITAT.pie` <- grid.arrange(`02.02_TRACKPLATES.HABITAT.GRASSLAND.pie`, `02.02_TRACKPLATES.HABITAT.WFS.pie`, nrow = 1)
rm(`02.02_TRACKPLATES.HABITAT.WFS.pie`, `02.02_TRACKPLATES.HABITAT.GRASSLAND.pie`)

# 02.02 - BOXPLOT HABITAT & LIGHT TREATMENT - PROPORTION
#-------------------------------------------------------

# REMOVE NA's
SUBSET <- SUBSET[!is.na(SUBSET$SLUG_TRACKS_PROP),] # 605

# ONLY KEEP POSITIVE PLATES
SUBSET <- SUBSET[SUBSET$SLUG_TRACKS_PROP > 0,] # 316

`02.02_TRACKPLATES.HABITAT.box` <- ggplot(
  data = SUBSET,
  aes(
    x = HABITAT,
    y = SLUG_TRACKS_PROP,
    fill = HABITAT,
    pattern = PLATE_LOC)) +
  geom_boxplot_pattern(
    pattern_color = "burlywood",
    pattern_fill = "burlywood",
    pattern_angle = 45,
    pattern_density = 0.25,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(alpha = 0.3) +
  scale_pattern_manual(
    values = c("CLOSE" = "stripe", "FAR"  = "none"),
    name = "Treatment",
    labels = c("dark", "light")) +
  scale_fill_manual(values = COLOR.PALETTE) +
  stat_compare_means(
    aes(
    group = PLATE_LOC),
    label = "p.format",
    size = 4,
    method = "t.test") +
  theme_minimal() +
  guides(fill = "none") +
  labs(
    x = "Habitat",
    y = "Proportion covered by tracks [%]") +
  theme(
    legend.position = c(0.1, 0.75),
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`02.02_TRACKPLATES.HABITAT.box`)

# SAVE
# ggsave(filename = paste0("02.02_TRACKPLATES.HABITAT.pie.jpeg"),
         # plot = `02.02_TRACKPLATES.HABITAT.pie`, path = HOME,
         # height = 12, width = 20, units = "cm")

# REMOVE
rm(`02.02_TRACKPLATES.HABITAT.box`, `02.02_TRACKPLATES.HABITAT.pie`)
rm(PIE)

##############################################################################################################

# COLOR PALETTE (DARK vs LIGHT)
COLOR.PALETTE <- c(wes_palettes$Rushmore1[4], wes_palettes$Rushmore1[1])

# 02.04 TEMP AS COVARIABLE
##########################

# SUBSET
SUBSET <- TRACKPLATES[!is.na(TRACKPLATES$SLUG_TRACKS_BIN),] # 1173
SUBSET <- SUBSET[SUBSET$PLATE_LOC == "CLOSE",] # 605
SUBSET <- SUBSET[SUBSET$HABITA == "WFS",] # 376

# TEMP x PROBABILTY OF FINDING TRACKS
#-----------------------------------

# BINOMIAL
mod.bin.TEMP <- glm(SLUG_TRACKS_BIN ~ LIGHT_TRMT * TEMP, data = SUBSET, family = binomial)

# PREDICT
lim.min <- min(SUBSET$TEMP)
lim.max <- max(SUBSET$TEMP)

# Create empty df
preddata  <- expand.grid("TEMP" = seq(lim.min, lim.max, 1), "LIGHT_TRMT" = as.factor(c("DARK", "LIGHT")))

# PREDICT
preds <- predict(mod.bin.TEMP, newdata = preddata , type = "link", se.fit = TRUE)

critval <- 1.96 ## approx 95% CI
upr <- preds$fit + (critval * preds$se.fit)
lwr <- preds$fit - (critval * preds$se.fit)
fit <- preds$fit

fit2 <- mod.bin.TEMP$family$linkinv(fit)
upr2 <- mod.bin.TEMP$family$linkinv(upr)
lwr2 <- mod.bin.TEMP$family$linkinv(lwr)

preddata$fit <- fit2
preddata$lwr <- lwr2 
preddata$upr <- upr2 

# PLOT
`02.04_TEMP.PROB.points` <- ggplot() +
  
  # FIT MODELS
  geom_ribbon(
    data = preddata,
    aes(
      x = TEMP,
      ymin = lwr,
      ymax = upr,
      colour = LIGHT_TRMT),
    alpha = 0.1) +
  geom_line(
    data = preddata,
    aes(
      x = TEMP,
      y = fit,
      colour = LIGHT_TRMT,
      linetype = "bold"),
    linewidth = 2) +

  # ADD POINTS
  geom_point(
    data = SUBSET,
    aes(
      x = TEMP,
      y = as.numeric(SLUG_TRACKS_BIN),
      colour = LIGHT_TRMT)) +

  # ADD AESTHETICS...
  theme_minimal() +
  labs(
    x = "Temp [°C]",
    y = "Slug presence on plates",
    colour = "Light treatment",
    title = "Temp & probability of finding slug tracks") +
  scale_colour_manual(values = COLOR.PALETTE) +
  scale_fill_manual(values = COLOR.PALETTE) +
  guides(
    linetype = "none",
    alpha = "none",
    fill = "none",
    size = "none") +
  theme(
    legend.position = c(0.2, 0.85),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 10, face = "bold"),
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 10, face = "bold"),
    axis.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 8))

rm(preddata, preds, critval, fit, fit2, lwr, lwr2, upr, upr2, lim.max, lim.min, mod.bin.TEMP)

#-------------------------------------------------------------------------------------------------------------

# TEMP x ABUNDANCE OF TRACKS
#---------------------------

# SUBSET
SUBSET <- TRACKPLATES[!is.na(TRACKPLATES$SLUG_TRACKS_PROP),] # 1173
SUBSET <- SUBSET[SUBSET$PLATE_LOC == "CLOSE",] # 596
SUBSET <- SUBSET[SUBSET$HABITA == "WFS",] # 376
# SUBSET <- SUBSET[SUBSET$SLUG_TRACKS_PROP > 0,] # 215

# RUN MODELS
lm.TEMP <- glm(SLUG_TRACKS_PROP ~ TEMP * LIGHT_TRMT, data = SUBSET)

# PREDICT
lim.min <- min(SUBSET$TEMP)
lim.max <- max(SUBSET$TEMP)

# Create empty df
preddata  <- expand.grid("TEMP" = seq(lim.min, lim.max, 1), "LIGHT_TRMT" = as.factor(c("DARK", "LIGHT")))

# PREDICT
preds <- predict(lm.TEMP, newdata = preddata , type = "link", se.fit = TRUE)

critval <- 1.96 ## approx 95% CI
upr <- preds$fit + (critval * preds$se.fit)
lwr <- preds$fit - (critval * preds$se.fit)
fit <- preds$fit

fit2 <- lm.TEMP$family$linkinv(fit)
upr2 <- lm.TEMP$family$linkinv(upr)
lwr2 <- lm.TEMP$family$linkinv(lwr)

preddata$fit <- fit2
preddata$lwr <- lwr2 
preddata$upr <- upr2 

`02.04_TEMP.ABUN.points` <- ggplot() +
  
  # FIT MODELS
  geom_ribbon(
    data = preddata,
    aes(
      x = TEMP,
      ymin = lwr,
      ymax = upr,
      colour = LIGHT_TRMT),
    alpha = 0.1) +
  geom_line(
    data = preddata,
    aes(
      x = TEMP,
      y = fit,
      colour = LIGHT_TRMT,
      linetype = "bold"),
    linewidth = 2) +

  # ADD POINTS
  geom_point(
    data = SUBSET, # 6 NA's
    aes(
      x = TEMP,
      y = SLUG_TRACKS_PROP,
      colour = LIGHT_TRMT)) +

  # ADD AESTHETICS...
  theme_minimal() +
  labs(
    x = "Temp [°C]",
    y = "Proportion of plates cover by slugs",
    colour = "Light treatment",
    title = "Proportion of slugs tracks on plates") +
  scale_colour_manual(values = COLOR.PALETTE) +
  scale_fill_manual(values = COLOR.PALETTE) +
  guides(
    linetype = "none",
    alpha = "none",
    fill = "none",
    size = "none") +
  theme(
    legend.position = c(0.2, 0.85),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 10, face = "bold"),
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 10, face = "bold"),
    axis.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 10, face = "bold"),
    axis.text.y = element_text(size = 8))

rm(fit, lim.max, lim.min, lm.TEMP)

# MERGE & REMOVE
`02.04_TEMP.points` <- grid.arrange(`02.04_TEMP.PROB.points`, `02.04_TEMP.ABUN.points`, nrow = 1)
rm(`02.04_TEMP.ABUN.points`, `02.04_TEMP.points`, `02.04_TEMP.PROB.points`)

```

# 02.1 - TRACKPLATES / MODELS

```{r 02.1 TRACKPLATES MODELS, fig.width = 10, message = FALSE, warning = FALSE}

SUBSET <- TRACKPLATES[TRACKPLATES$HABITAT == "WFS" & TRACKPLATES$PLATE_LOC == "CLOSE",] # 462
SUBSET <- SUBSET[SUBSET$SLUG_TRACKS_PROP > 0,] # 301

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "AIC" = 9999,
  "d.AIC" = 9999)

# TWO VARIABLES
#--------------

#mod2.1
mod2.1 <- lmer(SLUG_TRACKS_PROP ~ LIGHT_TRMT * TEMP + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET)

Model <- "mod2.1"
Variable <- "LIGHT * TEMP"
AIC <- AIC(mod2.1)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1)

#mod2.2
mod2.2 <- lmer(SLUG_TRACKS_PROP ~ LIGHT_TRMT + TEMP + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET)

Model <- "mod2.2"
Variable <- "LIGHT + TEMP"
AIC <- AIC(mod2.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1)
rm(mod2.2)

# ONE VARIABLE
#-------------

# mod1.1 
mod1.1 <- lmer(SLUG_TRACKS_PROP ~ LIGHT_TRMT + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET)

Model <- "mod1.1"
Variable <- "LIGHT"
AIC <- AIC(mod1.1)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1)

# mod1.2
mod1.2 <- lmer(SLUG_TRACKS_PROP ~ TEMP + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET)

Model <- "mod1.2"
Variable <- "TEMP"
AIC <- AIC(mod1.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.2)

# ZERO VARIABLE
#--------------

# mod0
mod0 <- lmer(SLUG_TRACKS_PROP ~ 1 + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET)

Model <- "mod0"
Variable <- "1"
AIC <- AIC(mod0)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod0)

#-------------------------------------------------------------------------------------------------------------

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){
  
  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)
  
}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

#-------------------------------------------------------------------------------------------------------------

# BEST MODELS - PROP
#-------------------

# mod 2.1 [BEST AIC]
mod2.1 <- lmer(sqrt(SLUG_TRACKS_PROP) ~ LIGHT_TRMT * TEMP + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET)

`02.1_mod2.1.tbl` <- tbl_regression(mod2.1, 
                                    intercept = T,
                                    pvalue_fun = ~ style_pvalue(.x, digits = 3),
                                    estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**SLUG_TRACKS_PROP.sqrt ~ LIGHT * DATE_DOY + (1|STUDY SITE) + (1|YEAR)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(`02.1_mod2.1.tbl`)
# print(`02.1_mod2.1.tbl`)

# SAVE
# gtsave(as_gt(`02.1_mod2.1.tbl`),
#        file = file.path(paste0(HOME,"/02.1_mod2.1.tbl.png")))

# REMOVE
rm(`02.1_mod2.1.tbl`, mod2.1)
rm(AIC.TABLE, AIC, AIC.min, dAIC, i, list, Model, Variable)

#-------------------------------------------------------------------------------------------------------------

SUBSET <- TRACKPLATES[TRACKPLATES$HABITAT == "WFS" & TRACKPLATES$PLATE_LOC == "CLOSE",] #462

# BEST MODELS - BINOMIAL
#-----------------------

# mod 2.1 [BEST AIC]
mod2.1 <- glmer(SLUG_TRACKS_BIN ~ LIGHT_TRMT * TEMP + (1|STUDY.SITE) + (1|SAMP_ID), data = SUBSET, family = binomial)

`02.1_mod2.1.tbl` <- tbl_regression(mod2.1, 
                                    intercept = T,
                                    pvalue_fun = ~ style_pvalue(.x, digits = 3),
                                    estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**SLUG_TRACKS_BIN ~ LIGHT * TEMP + (1|STUDY SITE) + (1|SAMP_ID)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(`02.1_mod2.1.tbl`)
# print(`02.1_mod2.1.tbl`)

rm(`02.1_mod2.1.tbl`, mod2.1)

# FINAL REMOVE
##############

rm(TRACKPLATES, SUBSET)

```

# 03.0 - HERBIVORY IN POTS / DATA FORMATING & EXPLORATORY PLOTS

```{r 03.0 HERBIVORY IN POTS DATA FORMATING & EXPLORATORY PLOTS, fig.width = 10, message = FALSE, warning = FALSE}

# 03.0 FORMAT DATA
##################

# ADD LIGHT TREATMENT
#--------------------
CEPO$S_LIGHT_TRMT <- NA

for(i in (1:nrow(CEPO))){
  
  i.STU_SI <- CEPO$S_STU.SI[i]
  ifelse(
    
    # STATEMENT
    i.STU_SI %in% LIT.SITE,
    
    # IF YES
    CEPO$S_LIGHT_TRMT[i] <- "LIT",
    
    # IF NO
    CEPO$S_LIGHT_TRMT[i] <- "DARK")}

rm(i.STU_SI, i)

#-------------------------------------------------------------------------------------------------------------

# DATE
#-----
CEPO$S_DATE <- str_replace_all(CEPO$S_DATE, "-", "/")
CEPO$S_DATE <- str_replace_all(CEPO$S_DATE, "2023", "23")
CEPO$S_DATE <- str_replace_all(CEPO$S_DATE, "/23", "/2023")

CEPO$S_DATE <- as.Date(CEPO$S_DATE, format = "%d/%m/%Y", origin = "01/01/1970")
CEPO$S_DATE_DOY <- yday(CEPO$S_DATE)

#-------------------------------------------------------------------------------------------------------------

# ADD ABIOTIC
#############

CEPO$TEMP <- NA
CEPO$RAIN <- NA

# SAMP ID (+1 because recovered the day after!)
#----------------------------------------------
CEPO$S_DATE <- as.Date(CEPO$S_DATE, format = "%d-%m-%y")
CEPO$SAMP_ID_AFTER <- format(CEPO$S_DATE  + 1, format = "%y%m%d")
CEPO$SAMP_ID <- format(CEPO$S_DATE, format = "%y%m%d")

# REMOVE OLD SAMP ID
CEPO$S_SAMP.ID <- NULL

for(i in (1:nrow(CEPO))){

  # i <- 43
  
  ifelse(
    
    # ARGUMENT
    CEPO$S_TIME.PER[i] == "NIGHT",
    
    # IF YES = NIGHT
    {i.SAMP_ID <- CEPO$SAMP_ID_AFTER[i]
     i.ABIOTIC <- ABIOTIC[ABIOTIC$DATE == i.SAMP_ID,]
     CEPO$RAIN[i] <- i.ABIOTIC$RAIN_SUM12H[i.ABIOTIC$TIME == "08h00"]
     CEPO$TEMP[i] <- i.ABIOTIC$TEMP_12H[i.ABIOTIC$TIME == "08h00"]},
    
    # IF NO = DAY
    {i.SAMP_ID <- CEPO$SAMP_ID[i]
     i.ABIOTIC <- ABIOTIC[ABIOTIC$DATE == i.SAMP_ID,]
     CEPO$RAIN[i] <- i.ABIOTIC$RAIN_SUM12H[i.ABIOTIC$TIME == "20h00"]
     CEPO$TEMP[i] <- i.ABIOTIC$TEMP_12H[i.ABIOTIC$TIME == "20h00"]})
  
}

rm(i, i.SAMP_ID, i.ABIOTIC)

#-------------------------------------------------------------------------------------------------------------

# RAIN BINOMIAL
CEPO$RAIN_BIN <- NA

for(i in (1:nrow(CEPO))){
  
  ifelse(
    
    # ARGUMENT
    CEPO$RAIN[i] > 0,
    
    # IF YES
    CEPO$RAIN_BIN[i] <- "YES",

    # IF NO
    CEPO$RAIN_BIN[i] <- "NO")
  
}

#-------------------------------------------------------------------------------------------------------------

# HERBIVORY METRICS - LEA PROP & LEA ABS
########################################

CEPO$LEA.PROP <- NA
CEPO$LEA_ABS <- NA
CEPO$LEA.SEVER <- NA

# THRESHOLD <- 0
THRESHOLD <- 0.1

# FOR LOOP
for(i in (1:nrow(CEPO))){
  
  # i <- 79
  # print(CEPO$P_PL_LABEL[i])
  
  i.CEPO <- CEPO[i,]
  
  # LEAVE DAMAGES PROPORTION
  #-------------------------
  
    # BEFORE
    zero.ls.BEF <- c(i.CEPO$LEA_DAM0_BEFORE, i.CEPO$LEA_DAM1_BEFORE, i.CEPO$LEA_DAM2_BEFORE, i.CEPO$LEA_DAM3_BEFORE, 
                     i.CEPO$LEA_DAM4_BEFORE, i.CEPO$LEA_DAM5_BEFORE, i.CEPO$LEA_DAM6_BEFORE, i.CEPO$LEA_DAM7_BEFORE, 
                     i.CEPO$LEA_DAM8_BEFORE, i.CEPO$LEA_DAM9_BEFORE)
    
    zero.ls.BEF.n <- length(zero.ls.BEF[!is.na(zero.ls.BEF)])
    i.LEA.PROP.BEF <- 1 - ((length(zero.ls.BEF[zero.ls.BEF <= THRESHOLD & !is.na(zero.ls.BEF)])) / zero.ls.BEF.n)
    
    # AFTER
    zero.ls.AFT <- c(i.CEPO$LEA_DAM0_AFTER, i.CEPO$LEA_DAM1_AFTER, i.CEPO$LEA_DAM2_AFTER, i.CEPO$LEA_DAM3_AFTER, 
                     i.CEPO$LEA_DAM4_AFTER, i.CEPO$LEA_DAM5_AFTER, i.CEPO$LEA_DAM6_AFTER, i.CEPO$LEA_DAM7_AFTER, 
                     i.CEPO$LEA_DAM8_AFTER, i.CEPO$LEA_DAM9_AFTER)
    
    zero.ls.AFT.n <- length(zero.ls.AFT[!is.na(zero.ls.AFT)])  
    i.LEA.PROP.AFT <- 1 - ((length(zero.ls.AFT[zero.ls.AFT <= THRESHOLD & !is.na(zero.ls.AFT)])) / zero.ls.AFT.n)
  
    # DIFFERENCE
    CEPO$LEA.PROP[i] <- i.LEA.PROP.AFT - i.LEA.PROP.BEF
    
    # NEGATIVE, REPLACED WITH 0
    ifelse(
    
      # ARGUMENT
      CEPO$LEA.PROP[i] < 0,
      
      # IF YES
      CEPO$LEA.PROP[i] <- 0,
      
      # IF NO
      CEPO$LEA.PROP[i] <- CEPO$LEA.PROP[i])
  
  # ABSOLUTE NUMBER OF EATEN LEAVES
  #--------------------------------
  
    # BEFORE
    zero.ls.BEF.n <- length(zero.ls.BEF[!is.na(zero.ls.BEF) & zero.ls.BEF > THRESHOLD])
      
    # AFTER
    zero.ls.AFT.n <- length(zero.ls.AFT[!is.na(zero.ls.BEF) & zero.ls.AFT > THRESHOLD])
  
    # DIFFERENCE
    CEPO$LEA_ABS[i] <- zero.ls.AFT.n - zero.ls.BEF.n
    
    # NEGATIVE, REPLACED WITH 0
    ifelse(
    
      # ARGUMENT
      CEPO$LEA_ABS[i] < 0,
      
      # IF YES
      CEPO$LEA_ABS[i] <- 0,
      
      # IF NO
      CEPO$LEA_ABS[i] <- CEPO$LEA_ABS[i])
    
  # LEAVE SEVERITY
  #---------------
  
  # BEFORE
  ifelse(

    # ARGUMENT
    mean(zero.ls.BEF, na.rm = T) == 0,

    # IF YES
    i.LEA.SEVER.BEF <- 0,

    # IF NO
    i.LEA.SEVER.BEF <- mean(zero.ls.BEF[which(zero.ls.BEF > THRESHOLD)], na.rm = T))    

  # AFTER
  ifelse(

    # ARGUMENT
    mean(zero.ls.AFT, na.rm = T) == 0,

    # IF YES
    i.LEA.SEVER.AFT <- 0,

    # IF NO
    i.LEA.SEVER.AFT <- mean(zero.ls.AFT[which(zero.ls.AFT > THRESHOLD)], na.rm = T))
  
  # DIFFERENCE
  CEPO$LEA.SEVER[i] <- i.LEA.SEVER.AFT - i.LEA.SEVER.BEF
  
  # NEGATIVE, REPLACED WITH 0
  ifelse(
    
    # ARGUMENT
    CEPO$LEA.SEVER[i] < 0,
    
    # IF YES
    CEPO$LEA.SEVER[i] <- 0,
    
    # IF NO
    CEPO$LEA.SEVER[i] <- CEPO$LEA.SEVER[i])

}

rm(i.CEPO, i, i.LEA.PROP.AFT, i.LEA.PROP.BEF, i.LEA.SEVER.AFT, i.LEA.SEVER.BEF, THRESHOLD)
rm(zero.ls.AFT, zero.ls.AFT.n, zero.ls.BEF, zero.ls.BEF.n)

# EATEN LEAVES BINOMIAL
CEPO$LEA_ABS_BIN <- NA

for(i in (1:nrow(CEPO))){
  
  ifelse(
    
    # ARGUMENT
    CEPO$RAIN[i] > 0,
    
    # IF YES
    CEPO$LEA_ABS_BIN[i] <- 1,

    # IF NO
    CEPO$LEA_ABS_BIN[i] <- 0)
  
}
#-------------------------------------------------------------------------------------------------------------

# HERBIVORY METRICS - LEA SEVERITY
##################################

DAMAGE <- data.frame(
    
    LABEL = NA,
    DAY = NA,
    SAMPLING = NA,
    TREA_TIME = NA,
    TREA_LIGHT = NA,
    STUDY_SITE = NA,
    TEMP = NA,
    RAIN = NA,
    DAMAGES = NA)

# FOR LOOP
#----------
for(i in (1:nrow(CEPO))){
  
  # i <- 45
  # print(i)
  
  i.CEPO <- CEPO[i,]
  i.LABEL <- i.CEPO$P_PL_LABEL

  # EMPTY DATA FRAME
  #-----------------
  i.DAMAGE <- DAMAGE[1,]
  
  # FILL DAMAGES
  #-------------
  i.DAMAGES.AFT <- sort(c(i.CEPO$LEA_DAM0_AFTER, i.CEPO$LEA_DAM1_AFTER, i.CEPO$LEA_DAM2_AFTER, i.CEPO$LEA_DAM3_AFTER, 
                          i.CEPO$LEA_DAM4_AFTER, i.CEPO$LEA_DAM5_AFTER, i.CEPO$LEA_DAM6_AFTER, i.CEPO$LEA_DAM7_AFTER, 
                          i.CEPO$LEA_DAM8_AFTER, i.CEPO$LEA_DAM9_AFTER))
  
  i.DAMAGES.BEF <- sort(c(i.CEPO$LEA_DAM0_BEFORE, i.CEPO$LEA_DAM1_BEFORE, i.CEPO$LEA_DAM2_BEFORE, i.CEPO$LEA_DAM3_BEFORE, 
                          i.CEPO$LEA_DAM4_BEFORE, i.CEPO$LEA_DAM5_BEFORE, i.CEPO$LEA_DAM6_BEFORE, i.CEPO$LEA_DAM7_BEFORE, i.CEPO$LEA_DAM8_BEFORE, i.CEPO$LEA_DAM9_BEFORE))
  
  i.DAMAGES <- i.DAMAGES.AFT - i.DAMAGES.BEF
  
  # REPEAT THE EMPTY DATAFRAME N TIMES (N = length(i.DAMAGES))
  #-----------------------------------------------------------
  i.DAMAGE <- i.DAMAGE[rep(seq_len(nrow(i.DAMAGE)), length(i.DAMAGES)), ]
  i.DAMAGE$DAMAGES <- i.DAMAGES

  # FILL SAMPLING INFOS
  #--------------------
  i.DAMAGE$LABEL <- i.LABEL
  i.DAMAGE$DAY <- as.Date(i.CEPO$S_DATE)
  i.DAMAGE$SAMPLING <- as.character(i.CEPO$SAMP_ID_AFTER)
  i.DAMAGE$TREA_TIME <- i.CEPO$S_TIME.PER
  i.DAMAGE$TREA_LIGHT <- i.CEPO$S_LIGHT_TRMT
  i.DAMAGE$TREA_LIGHT <- i.CEPO$S_LIGHT_TRMT
  i.DAMAGE$STUDY_SITE <- i.CEPO$S_STU.SI
  i.DAMAGE$TEMP <- (i.CEPO$TEMP_AFTER + i.CEPO$TEMP_BEFORE) / 2
  i.DAMAGE$RAIN <- (i.CEPO$RAIN_3H_AFTER + i.CEPO$RAIN_3H_BEFORE) / 2

  # MERGE
  DAMAGE <- rbind(DAMAGE, i.DAMAGE)
  
}

rm(i.CEPO, i.DAMAGE, i, i.DAMAGES, i.LABEL, i.DAMAGES.AFT, i.DAMAGES.BEF)

# CLEAN
#------

# Remove first line full of NA's 
DAMAGE <- DAMAGE[-1,] # 4170

# Remove NA's
DAMAGE <- DAMAGE[!is.na(DAMAGE$DAMAGES),] # 3645

# Transform negative into zeroes
for(i in (1:nrow(DAMAGE))){
  
  ifelse(
      
    # ARGUMENT
    DAMAGE$DAMAGES[i] < 0,
    
    # IF YES
    DAMAGE$DAMAGES[i] <- 0,
    
    # IF NO
    DAMAGE$DAMAGES[i] <- DAMAGE$DAMAGES[i])  
  
}

# Remove zeroes
DAMAGE <- DAMAGE[DAMAGE$DAMAGES > 0,] # 742

# RAIN BINOMIAL
DAMAGE$RAIN_BIN <- NA

for(i in (1:nrow(DAMAGE))){
  
  ifelse(
    
    # ARGUMENT
    DAMAGE$RAIN[i] > 0,
    
    # IF YES
    DAMAGE$RAIN_BIN[i] <- "YES",

    # IF NO
    DAMAGE$RAIN_BIN[i] <- "NO")
  
}

```

# 03.1 - HERBIVORY IN POTS / MODELS 

```{r 03.1 HERBIVORY IN POTS MODELS, fig.width = 10, message = FALSE, warning = FALSE}

SUBSET <- CEPO

# 03.11 - NUMBER OF EATEN LEAVES
################################

`03.11_ABS_LEA` <- ggplot(data = SUBSET,
    aes(
      x = LEA_ABS,
      y = S_TIME.PER,
      fill = S_TIME.PER,
      pattern = S_LIGHT_TRMT)) +
  geom_boxplot_pattern(color = "black",
    pattern_fill = "burlywood",
    pattern_angle = 45,
    pattern_density = 0.5,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(alpha = 0.3) +
  scale_pattern_manual(
    values = c("LIT" = "stripe", "DARK"  = "none"),
    name = "Treatment",
    labels = c("Dark", "Light")) +
  scale_fill_manual(values = c("white", "grey50")) +
  theme_minimal() +
  guides(fill = "none") +
  labs(
    title = "Number of leaves with fresh damages \nafter 12 h of treatment",
    x = "Number of damaged leaves",
    y = "Time period") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.position = c(0.9, 0.9),
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`03.11_ABS_LEA`)
# ggsave(filename = "03.11_ABS_LEA.jpeg",
#          plot = `03.11_ABS_LEA`, path = HOME,
#          height = 8, width = 16, units = "cm")

# REMOVE
rm(`03.11_ABS_LEA`)

#-------------------------------------------------------------------------------------------------------------

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "AIC" = 9999,
  "d.AIC" = 9999)

# THREE COVARIABLES
#------------------

# mod3.1
mod3.1 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER * S_LIGHT_TRMT * TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod3.1"
Variable <- "S_TIME.PER * S_LIGHT_TRMT * TEMP"
AIC <- AIC(mod3.1)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.1)

# mod3.2
mod3.2 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER + S_LIGHT_TRMT + TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod3.2"
Variable <- "S_TIME.PER + S_LIGHT_TRMT + TEMP"
AIC <- AIC(mod3.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.2)

# mod3.3
mod3.3 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER * S_LIGHT_TRMT + TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod3.3"
Variable <- "S_TIME.PER * S_LIGHT_TRMT + TEMP"
AIC <- AIC(mod3.3)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.3)

# mod3.4
mod3.4 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER + S_LIGHT_TRMT * TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod3.4"
Variable <- "S_TIME.PER + S_LIGHT_TRMT * TEMP"
AIC <- AIC(mod3.4)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.4)

# TWO VARIABLES
#--------------

#mod2.1
mod2.1 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER * S_LIGHT_TRMT + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod2.1"
Variable <- "S_TIME.PER * S_LIGHT_TRMT"
AIC <- AIC(mod2.1)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1)

#mod2.2
mod2.2 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER + S_LIGHT_TRMT + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod2.2"
Variable <- "S_TIME.PER + S_LIGHT_TRMT"
AIC <- AIC(mod2.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2)

#mod2.3
mod2.3 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER * TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod2.3"
Variable <- "S_TIME.PER * TEMP"
AIC <- AIC(mod2.3)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.3)

#mod2.4
mod2.4 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER + TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod2.4"
Variable <- "S_TIME.PER + TEMP"
AIC <- AIC(mod2.4)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.4)

#mod2.5
mod2.5 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_LIGHT_TRMT * TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod2.5"
Variable <- "S_LIGHT_TRMT * TEMP"
AIC <- AIC(mod2.5)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.5)

#mod2.6
mod2.6 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_LIGHT_TRMT + TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod2.6"
Variable <- "S_LIGHT_TRMT + TEMP"
AIC <- AIC(mod2.6)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.6)

# ONE VARIABLE
#-------------

# mod1.1 
mod1.1 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod1.1"
Variable <- "S_TIME.PER"
AIC <- AIC(mod1.1)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1)

# mod1.2
mod1.2 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_LIGHT_TRMT + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod1.2"
Variable <- "S_LIGHT_TRMT"
AIC <- AIC(mod1.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.2)

# mod1.3
mod1.3 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod1.3"
Variable <- "TEMP"
AIC <- AIC(mod1.3)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.3)

# ZERO VARIABLE
#--------------

# mod0
mod0 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ 1 + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family = binomial)

Model <- "mod0"
Variable <- "1"
AIC <- AIC(mod0)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod0)

#-------------------------------------------------------------------------------------------------------------

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){
  
  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)
  
}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

#-------------------------------------------------------------------------------------------------------------

# BEST MODELS (mod 3.3)
#----------------------

# mod 3.3 [BEST AIC]
mod03.11 <- glmer(cbind(LEA_ABS, 10 - LEA_ABS) ~ S_TIME.PER * S_LIGHT_TRMT + TEMP + (1|S_STU.SI) + (1|SAMP_ID_AFTER), data = SUBSET, family =binomial)

`mod03.11.tbl` <- tbl_regression(mod03.11, intercept = T) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**cbind(N DAMAGED LEAVES, 10 - N DAMAGED LEAVES) ~ LIGHT * TIME PERIOD + TEMP, fam = binomial**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(`mod03.11.tbl`)
# print(`mod03.11.tbl`)

# SAVE
# gtsave(as_gt(`mod03.11.tbl`),
#        file = file.path(paste0(HOME,"/mod03.11.tbl.png")))

# REMOVE
rm(`mod03.11.tbl`, mod03.11)
rm(AIC.TABLE, AIC, AIC.min, dAIC, i, list, Model, Variable)

##############################################################################################################

# 03.12 - SEVERITY OF DAMAGES
#############################

# SUBSET
#-------
SUBSET <- DAMAGE

# PLOT
#-----
`03.12_SEVER_LEA` <- ggplot(data = SUBSET, 
    aes(
      x = DAMAGES,
      y = TREA_TIME,
      fill = TREA_TIME,
      pattern = TREA_LIGHT)) +
  geom_boxplot_pattern(color = "black",
    pattern_fill = "burlywood",
    pattern_angle = 45,
    pattern_density = 0.5,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(alpha = 0.1) +
  scale_pattern_manual(
    values = c("LIT" = "stripe", "DARK"  = "none"),
    name = "Treatment",
    labels = c("Dark", "Light")) +
  scale_fill_manual(values = c("white", "grey50")) +
  theme_minimal() +
  scale_x_continuous(
    labels = scales::percent,
    limits = c(0, 1)) +
  guides(fill = "none") +
  labs(
    title = "Severity of damaged leaves \nafter 12 hours of treatment",
    x = "Severity of damages on leaves [%]",
    y = "Time period") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.position = c(0.9, 0.9),
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`03.12_SEVER_LEA`)
# ggsave(filename = "03.12_SEVER_LEA.jpeg",
#          plot = `03.12_SEVER_LEA`, path = HOME,
#          height = 8, width = 16, units = "cm")

# REMOVE
rm(`03.12_SEVER_LEA`)

#-------------------------------------------------------------------------------------------------------------

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "anova.p" = 9999,
  "anova.dAIC" = 9999,
  "AIC" = 9999,
  "BIC" = 9999)

# THREE COVARIABLES
#------------------

# mod3.1
mod3.1.light <- lmer(DAMAGES ~ TREA_LIGHT * TREA_TIME * TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod3.1 <- lmer(DAMAGES ~ TREA_TIME * TEMP + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod3.1"
Variable <- "TREA_LIGHT * TREA_TIME * TEMP"

anova <- anova(mod3.1, mod3.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.1, mod3.1.light)

# mod3.2
mod3.2.light <- lmer(DAMAGES ~ TREA_LIGHT + TREA_TIME + TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod3.2 <- lmer(DAMAGES ~ TREA_TIME + TEMP + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod3.2"
Variable <- "TREA_LIGHT + TREA_TIME + TEMP"

anova <- anova(mod3.2, mod3.2.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.2, mod3.2.light)

# mod3.3
mod3.3.light <- lmer(DAMAGES ~ TREA_LIGHT * TREA_TIME + TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod3.3 <- lmer(DAMAGES ~ TREA_TIME + TEMP + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod3.3"
Variable <- "TREA_LIGHT * TREA_TIME + TEMP"

anova <- anova(mod3.3, mod3.3.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.3, mod3.3.light)

# mod3.4
mod3.4.light <- lmer(DAMAGES ~ TREA_LIGHT + TREA_TIME * TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod3.4 <- lmer(DAMAGES ~ TREA_TIME * TEMP + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod3.4"
Variable <- "TREA_LIGHT + TREA_TIME * TEMP"

anova <- anova(mod3.4, mod3.4.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.4, mod3.4.light)

# TWO VARIABLES
#--------------

#mod2.1 TREA_LIGHT * TREA_TIME
mod2.1.light <- lmer(DAMAGES ~ TREA_LIGHT * TREA_TIME + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod2.1 <- lmer(DAMAGES ~ TREA_TIME + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod2.1"
Variable <- "TREA_LIGHT * TREA_TIME"

anova <- anova(mod2.1, mod2.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1, mod2.1.light)

#mod2.2 TREA_LIGHT + TREA_TIME
mod2.2.light <- lmer(DAMAGES ~ TREA_LIGHT + TREA_TIME + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod2.2 <- lmer(DAMAGES ~ TREA_TIME + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod2.2"
Variable <- "TREA_LIGHT + TREA_TIME"

anova <- anova(mod2.2, mod2.2.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2, mod2.2.light)

#mod2.3 TREA_LIGHT * TEMP
mod2.3.light <- lmer(DAMAGES ~ TREA_LIGHT * TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod2.3 <- lmer(DAMAGES ~ TEMP + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod2.3"
Variable <- "TREA_LIGHT * TEMP"

anova <- anova(mod2.3, mod2.3.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.3, mod2.3.light)

#mod2.4 TREA_LIGHT + TEMP
mod2.4.light <- lmer(DAMAGES ~ TREA_LIGHT + TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod2.4 <- lmer(DAMAGES ~ TEMP + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod2.4"
Variable <- "TREA_LIGHT + TEMP"

anova <- anova(mod2.4, mod2.4.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.4, mod2.4.light)

# ONE VARIABLE 
#-------------

# mod1.1 TREA_LIGHT
mod1.1.light <- lmer(DAMAGES ~ TREA_LIGHT + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
mod1.1 <- lmer(DAMAGES ~ 1 + (1|LABEL) + (1|STUDY_SITE), data = SUBSET)

Model <- "mod1.1"
Variable <- "TREA_LIGHT"

anova <- anova(mod1.1, mod1.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1, mod1.1.light)

rm(anova, anova.dAIC, anova.p, BIC, THRESHOLD)

#-------------------------------------------------------------------------------------------------------------

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]
AIC.TABLE$d.AIC <- NA

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){
  
  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)
  
}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

#-------------------------------------------------------------------------------------------------------------

# BEST MODELS
#------------

# mod 3.1
mod03.12 <- lmer(log(DAMAGES) ~ TREA_LIGHT * TREA_TIME + TEMP + (1|LABEL) + (1|STUDY_SITE) + (1|SAMPLING), data = SUBSET)
res <- residuals(mod03.12)
qqnorm(res)
qqline(res)

mod03.12.tbl <- tbl_regression(mod03.12, intercept = T) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**DAM LEAVES ~ LIGHT * TIME PERIOD + TEMP**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(mod03.12.tbl)
# print(mod03.12.tbl)

# SAVE
# gtsave(as_gt(`03.11_mod3.1.light.tbl`),
#        file = file.path(paste0(HOME,"/03.11_mod3.1.light.tbl.png")))

# REMOVE
rm(mod03.12, mod03.12.tbl)
rm(AIC.TABLE, AIC, AIC.min, i, list, Model, Variable)

#-------------------------------------------------------------------------------------------------------------

# FINAL REMOVE
##############

rm(CEPO, DAMAGE)

```

# 04.0 - SLUGS TRANSECTS / DATA FORMATING

```{r 04.0 SLUGS TRANSECTS DATA FORMATING, fig.width = 10, message = FALSE, warning = FALSE}

# 04.0 REFORMAT (N SLUGS PER LIGHT DISTANCE)
#############################################

# GENUS SNAIL:
INTERACTIONS$GENUS[INTERACTIONS$ART_GROUP == "SNAIL"] <- "Snail"

# SAMPLING LONG
INTERACTIONS.ALL$SAMPLING.LONG <- paste0(INTERACTIONS.ALL$SAMPLING, ".", INTERACTIONS.ALL$SEGMENT)

# STUDY_SITE.YEAR
YEAR.ls <- c(rep(".22", length(DARK.SITE.22)), rep(".23", length(DARK.SITE)))
SITE.ls <- c(DARK.SITE.22, DARK.SITE)
DARK.ALL <- as.data.frame(cbind(SITE.ls, YEAR.ls))
DARK.ALL.ls <- paste0(DARK.ALL$SITE.ls, DARK.ALL$YEAR.ls)
rm(YEAR.ls, SITE.ls, DARK.ALL)

# EMPTY DATA FRAME
SAMPLING.HERB <- data.frame(
    
    YEAR = NA,
    SP = NA,
    STUDY_SITE = NA,
    TIME = NA,
    ARION = NA,
    DEROCERAS = NA,
    SNAIL = NA,
    HERBIVORE = NA,
    LIGHT = NA,
    DISTANCE = NA,
    SAMPLING = NA,
    TEMP = NA,
    RAIN = NA,
    AREA = NA,
    STUDY_SITE.YEAR = NA)

# FOR LOOP
#---------
for(i in (1:length(SAMPLING.ls))){
  
  # i <- 25
  
  i.SAMPLING.HERB <- SAMPLING.HERB[1,]
  i.SAMPLING.HERB[(1:4)] <- strsplit(SAMPLING.ls, ".", fixed = TRUE)[[i]][(1:4)]
  i.SAMPLING.HERB$SAMPLING <- paste0(i.SAMPLING.HERB$YEAR,
                                     ".",
                                     i.SAMPLING.HERB$SP,
                                     ".",
                                     i.SAMPLING.HERB$STUDY_SITE,
                                     ".",
                                     i.SAMPLING.HERB$TIME)
  
  i.SAMPLING.HERB$TEMP <- mean(INTERACTIONS.ALL$TEMP[INTERACTIONS.ALL$SAMPLING == i.SAMPLING.HERB$SAMPLING])
  i.SAMPLING.HERB$RAIN <- mean(INTERACTIONS.ALL$RAIN[INTERACTIONS.ALL$SAMPLING == i.SAMPLING.HERB$SAMPLING])
  i.SAMPLING.HERB$STUDY_SITE.YEAR <- paste0(i.SAMPLING.HERB$STUDY_SITE, ".", i.SAMPLING.HERB$YEAR)
  
  i.SAMPLING.HERB <- do.call("rbind", replicate(3, i.SAMPLING.HERB, simplify = FALSE)) 
  
  i.SAMPLING.HERB$DISTANCE[1] <- "CLOSE"
  i.SAMPLING.HERB$DISTANCE[2] <- "MIDDLE"
  i.SAMPLING.HERB$DISTANCE[3] <- "FAR"
  
  ifelse(
    
    # ARGUMENT
    unique(i.SAMPLING.HERB$STUDY_SITE.YEAR ) %in% DARK.ALL.ls,
    
    # IF YES
    i.SAMPLING.HERB$LIGHT <- "DARK",
    
    # IF NO
    i.SAMPLING.HERB$LIGHT <- "LIGHT")

  # 2022
  ######
  
  # STANDARD
  #---------
  
  ifelse(
    
    # ARGUMENT
    unique(i.SAMPLING.HERB$YEAR) == "22",

      # IF YES
      {
      
      # CLOSE    
      i.SAMPLING.HERB$ARION[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T02", "P04", "P01") &
        INTERACTIONS$GENUS == "Arion",])
      
      i.SAMPLING.HERB$DEROCERAS[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T02", "P04", "P01") &
        INTERACTIONS$GENUS == "Deroceras",])
         
      i.SAMPLING.HERB$SNAIL[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T02", "P04", "P01") &
        INTERACTIONS$GENUS == "Snail",])
      
      i.SAMPLING.HERB$AREA[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- 25

      # FAR    
      i.SAMPLING.HERB$ARION[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T03" ,"T04", "P02", "P03") &
        INTERACTIONS$GENUS == "Arion",])
         
      i.SAMPLING.HERB$DEROCERAS[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T03" ,"T04", "P02", "P03") &
        INTERACTIONS$GENUS == "Deroceras",])
      
      i.SAMPLING.HERB$SNAIL[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T03" ,"T04", "P02", "P03") &
        INTERACTIONS$GENUS == "Snail",])
      
      i.SAMPLING.HERB$AREA[i.SAMPLING.HERB$DISTANCE == "FAR"] <- 25
      
      },
    
      # IF NO
      
      {
      
      i.SAMPLING.HERB$ARION <- i.SAMPLING.HERB$ARION
      i.SAMPLING.HERB$DEROCERAS <- i.SAMPLING.HERB$DEROCERAS
      i.SAMPLING.HERB$SNAIL <- i.SAMPLING.HERB$SNAIL
      i.SAMPLING.HERB$AREA <- i.SAMPLING.HERB$AREA

      }
  )    

  # SHORT TRANSECT
  #---------------

  ifelse(
    
    # ARGUMENT
    unique(i.SAMPLING.HERB$YEAR) == "22" & unique(i.SAMPLING.HERB$STUDY_SITE) %in% c("PIZZA", "OAK"),

      # IF YES
      {
      
      # CLOSE    
      i.SAMPLING.HERB$ARION[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T02", "T03", "P01", "P04") &
        INTERACTIONS$GENUS == "Arion",])
         
      i.SAMPLING.HERB$DEROCERAS[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T02", "T03", "P01", "P04") &
        INTERACTIONS$GENUS == "Deroceras",])
      
      i.SAMPLING.HERB$SNAIL[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T02", "T03", "P01", "P04") &
        INTERACTIONS$GENUS == "Snail",])
      
      i.SAMPLING.HERB$AREA[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- 20
      
      # FAR    
      i.SAMPLING.HERB$ARION[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T05", "TO6", "T07", "T04", "P02", "P03") &
        INTERACTIONS$GENUS == "Arion",])
         
      i.SAMPLING.HERB$DEROCERAS[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T05", "TO6", "T07", "T04", "P02", "P03") &
        INTERACTIONS$GENUS == "Deroceras",])
         
      i.SAMPLING.HERB$SNAIL[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T05", "TO6", "T07", "T04", "P02", "P03") &
        INTERACTIONS$GENUS == "Snail",])
      
      i.SAMPLING.HERB$AREA[i.SAMPLING.HERB$DISTANCE == "FAR"] <- 20
      
      },
    
      # IF NO
      {

      i.SAMPLING.HERB$ARION <- i.SAMPLING.HERB$ARION
      i.SAMPLING.HERB$DEROCERAS <- i.SAMPLING.HERB$DEROCERAS
      i.SAMPLING.HERB$SNAIL <- i.SAMPLING.HERB$SNAIL
      i.SAMPLING.HERB$AREA <- i.SAMPLING.HERB$AREA
      
      }
  )    
  
  # 2023
  ######
  
  ifelse(
    
    # ARGUMENT
    unique(i.SAMPLING.HERB$YEAR) == "23",

      # IF YES
      {
      
      # CLOSE    
      i.SAMPLING.HERB$ARION[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T04") &
        INTERACTIONS$GENUS == "Arion",])
         
      i.SAMPLING.HERB$DEROCERAS[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T04") &
        INTERACTIONS$GENUS == "Deroceras",])
      
      i.SAMPLING.HERB$SNAIL[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T01", "T04") &
        INTERACTIONS$GENUS == "Snail",])      
      i.SAMPLING.HERB$AREA[i.SAMPLING.HERB$DISTANCE == "CLOSE"] <- 16
      
      # FAR    
      i.SAMPLING.HERB$ARION[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T02", "T03") &
        INTERACTIONS$GENUS == "Arion",])
         
      i.SAMPLING.HERB$DEROCERAS[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T02", "T03") &
        INTERACTIONS$GENUS == "Deroceras",])

      i.SAMPLING.HERB$SNAIL[i.SAMPLING.HERB$DISTANCE == "FAR"] <- nrow(
        INTERACTIONS[INTERACTIONS$SAMPLING == unique(i.SAMPLING.HERB$SAMPLING) &
        INTERACTIONS$SEGMENT %in% c("T02", "T03") &
        INTERACTIONS$GENUS == "Snail",])

      i.SAMPLING.HERB$AREA[i.SAMPLING.HERB$DISTANCE == "FAR"] <- 16
      
      },
    
      # IF NO
      {
      
      i.SAMPLING.HERB$ARION <- i.SAMPLING.HERB$ARION
      i.SAMPLING.HERB$DEROCERAS <- i.SAMPLING.HERB$DEROCERAS
      i.SAMPLING.HERB$SNAIL <- i.SAMPLING.HERB$SNAIL
      i.SAMPLING.HERB$AREA <- i.SAMPLING.HERB$AREA    
      
      }
  )    

  # APPEND
  SAMPLING.HERB <- rbind(SAMPLING.HERB, i.SAMPLING.HERB)

}
    
# REMOVE FIRST LINE OF NA's
SAMPLING.HERB <- SAMPLING.HERB[-1,]
rm(i.SAMPLING.HERB, i)

# TOT N HERBIVORES
SAMPLING.HERB$HERBIVORE <- SAMPLING.HERB$ARION + SAMPLING.HERB$SNAIL + SAMPLING.HERB$DEROCERAS

# TOT SLUGS
SAMPLING.HERB$SLUG <- SAMPLING.HERB$ARION + SAMPLING.HERB$DEROCERAS

# REMOVE DUPLICATED VALUES
SAMPLING.HERB <- SAMPLING.HERB[!duplicated(SAMPLING.HERB), ]

# REMOVE MIDDLE
SAMPLING.HERB <- SAMPLING.HERB[!SAMPLING.HERB$DISTANCE == "MIDDLE",]

# CHANGE FACTOR LEVEL (CLOSE, FAR)
SAMPLING.HERB$DISTANCE <- as.factor(SAMPLING.HERB$DISTANCE)

#-------------------------------------------------------------------------------------------------------------

# ADD PAIRING
#------------
SAMPLING.HERB$PAIRS <- NA

for(i in (1:nrow(SAMPLING.HERB))){
  
  i.STUDY_SITE.YEAR <- SAMPLING.HERB$STUDY_SITE.YEAR[i]
  i.SP <- SAMPLING.HERB$SP[i]
  
  # 2022
  ifelse(i.STUDY_SITE.YEAR %in% c("ANTS.22", "BADGER.22"), 
         SAMPLING.HERB$PAIRS[i] <- "22.SOUTH", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])
  
  ifelse(i.STUDY_SITE.YEAR %in% c("DEER.22", "FOX.22"), 
         SAMPLING.HERB$PAIRS[i] <- "22.VULLY", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])  
  
  ifelse(i.STUDY_SITE.YEAR %in% c("JUNGLE.22", "OAK.22"), 
         SAMPLING.HERB$PAIRS[i] <- "22.SALAVAUX", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])   
  
  ifelse(i.STUDY_SITE.YEAR %in% c("PIZZA.22", "TRAIN II.22"), 
         SAMPLING.HERB$PAIRS[i] <- "22.NORTH", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])   
  
  ifelse(i.STUDY_SITE.YEAR %in% c("RABBIT.22", "KINGFISHER.22"), 
         SAMPLING.HERB$PAIRS[i] <- "22.SUGIEZ", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])   
  
  ifelse(i.STUDY_SITE.YEAR %in% c("STORK.22", "VOLE.22"), 
         SAMPLING.HERB$PAIRS[i] <- "22.AVENCHES", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])   

  # 2023
  ifelse(i.STUDY_SITE.YEAR %in% c("MARTEN.23", "BADGER.23"), 
         SAMPLING.HERB$PAIRS[i] <- "23.MUSTELID", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])     
  
  ifelse(i.STUDY_SITE.YEAR %in% c("ANTS.23", "HORNET.23"), 
         SAMPLING.HERB$PAIRS[i] <- "23.HYMENO", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])     
  
  ifelse(i.STUDY_SITE.YEAR %in% c("QUAIL.23", "UPUPA.23"), 
         SAMPLING.HERB$PAIRS[i] <- "23.WALKINGBIRD", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])
  
  ifelse(i.STUDY_SITE.YEAR %in% c("TOAD.23", "NEWT.23"), 
         SAMPLING.HERB$PAIRS[i] <- "23.AMPHIBIAN", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])
  
  ifelse(i.STUDY_SITE.YEAR %in% c("EAGLE.23", "PEREGRINE.23"), 
         SAMPLING.HERB$PAIRS[i] <- "23.RAPTOR", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])

  # 2023 - SP01 - SP03
  ifelse(i.STUDY_SITE.YEAR %in% c("LIZARD.23", "GRASS SNAKE.23") & i.SP %in% c("SP01", "SP02", "SP03"), 
         SAMPLING.HERB$PAIRS[i] <- "23.REPTILE", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])     
  
  ifelse(i.STUDY_SITE.YEAR %in% c("WOODPECKER.23", "YELFAR HAMMER.23") & i.SP %in% c("SP01", "SP02", "SP03"), 
         SAMPLING.HERB$PAIRS[i] <- "23.FLYINGBIRD", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])  
  
  ifelse(i.STUDY_SITE.YEAR %in% c("CHAMOIS.23", "DEER.23") & i.SP %in% c("SP01", "SP02", "SP03"), 
         SAMPLING.HERB$PAIRS[i] <- "23.UNGULATE", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])  

  # 2023 - SP04 - SP05
  ifelse(i.STUDY_SITE.YEAR %in% c("LIZARD.23", "WOODPECKER.23") & i.SP %in% c("SP04", "SP05"), 
         SAMPLING.HERB$PAIRS[i] <- "23.MIXED", SAMPLING.HERB$PAIRS[i] <- SAMPLING.HERB$PAIRS[i])     
  }

SAMPLING.HERB$PAIRS.SAMPLING <- paste0(SAMPLING.HERB$PAIRS, ".", SAMPLING.HERB$SP)

##############################################################################################################

# REMOVE SAMPLINGS WHERE NO HERBIVORES WHERE FOUND [BASED ON PAIRING]
#####################################################################

# SLUG
#-----
REMOVE.ls <- NA

for(i in unique(SAMPLING.HERB$PAIRS.SAMPLING)){
  
  i.HERBS.tot <- sum(SAMPLING.HERB$SLUG[SAMPLING.HERB$PAIRS.SAMPLING == i])
  
  ifelse(
    
    # ARGUMENT
    # i.HERBS.tot == 0,
    i.HERBS.tot < 2, 
    
    # IF YES
    REMOVE.ls <- append(REMOVE.ls, i),
    
    # IF NO
    REMOVE.ls <- REMOVE.ls)

}

REMOVE.ls <- REMOVE.ls[-1]

# REMOVE STUDY SITES
#-------------------
SAMPLING.SLUG <- SAMPLING.HERB[!SAMPLING.HERB$PAIRS.SAMPLING %in% REMOVE.ls,] # 96 samplings left
rm(REMOVE.ls, i.HERBS.tot, i, PAIRED.ls)

#-------------------------------------------------------------------------------------------------------------

# ARION
#------
REMOVE.ls <- NA

for(i in unique(SAMPLING.HERB$PAIRS.SAMPLING)){
  
  i.HERBS.tot <- sum(SAMPLING.HERB$ARION[SAMPLING.HERB$PAIRS.SAMPLING == i])
  
  ifelse(
    
    # ARGUMENT
    # i.HERBS.tot == 0,
    i.HERBS.tot < 2, 
    
    # IF YES
    REMOVE.ls <- append(REMOVE.ls, i),
    
    # IF NO
    REMOVE.ls <- REMOVE.ls)

}

REMOVE.ls <- REMOVE.ls[-1]

# REMOVE STUDY SITES
#-------------------
SAMPLING.ARION <- SAMPLING.HERB[!SAMPLING.HERB$PAIRS.SAMPLING %in% REMOVE.ls,] # 80 samplings left
rm(REMOVE.ls, i.HERBS.tot, i, PAIRED.ls)

#-------------------------------------------------------------------------------------------------------------

# Deroceras
#----------
REMOVE.ls <- NA

for(i in unique(SAMPLING.HERB$PAIRS.SAMPLING)){
  
  i.HERBS.tot <- sum(SAMPLING.HERB$DEROCERAS[SAMPLING.HERB$PAIRS.SAMPLING == i])
  
  ifelse(
    
    # ARGUMENT
    # i.HERBS.tot == 0,
    i.HERBS.tot < 2, 
    
    # IF YES
    REMOVE.ls <- append(REMOVE.ls, i),
    
    # IF NO
    REMOVE.ls <- REMOVE.ls)

}

REMOVE.ls <- REMOVE.ls[-1]

# REMOVE STUDY SITES
#-------------------
SAMPLING.DEROCERAS <- SAMPLING.HERB[!SAMPLING.HERB$PAIRS.SAMPLING %in% REMOVE.ls,] # 24 samplings left
rm(REMOVE.ls, i.HERBS.tot, i)

#-------------------------------------------------------------------------------------------------------------

# REFORMAT SAMPLING SLUGS (FOR FINAL MODEL)
#------------------------------------------

# Create a new variable for slug species
SAMPLING.SLUG$SPECIES <- NA

# Create an empty data frame
SAMPLING <- SAMPLING.SLUG[1,]
SAMPLING[1,] <- NA

# Fill empty data frame
for(i in (1:nrow(SAMPLING.SLUG))){
  
  # i <- 12
  
  i.SAMPLING.SLUG <- SAMPLING.SLUG[i,]
  i.SAMPLING.SLUG <- rbind(i.SAMPLING.SLUG, i.SAMPLING.SLUG)
  
  i.SAMPLING.SLUG$SPECIES[1] <- "D. reticulatum"
  i.SAMPLING.SLUG$SPECIES[2] <- "A. lusitanicus"

  i.SAMPLING.SLUG$SLUG[1] <- i.SAMPLING.SLUG$DEROCERAS[1]
  i.SAMPLING.SLUG$SLUG[2] <- i.SAMPLING.SLUG$ARION[1]
  
  SAMPLING <- rbind(SAMPLING, i.SAMPLING.SLUG)
  
}

SAMPLING <- SAMPLING[-1,]
SAMPLING <- SAMPLING[-1,]
SAMPLING <- SAMPLING[-1,]

# REMOVE USELESS VARIABLES
#-------------------------

SAMPLING$ARION <- NULL
SAMPLING$DEROCERAS <- NULL
SAMPLING$SNAIL <- NULL
SAMPLING$HERBIVORE <- NULL

rm(i.SAMPLING.SLUG, i, i.SP, i.STUDY_SITE.YEAR, SAMPLING.ls)
rm(SAMPLING.ARION, SAMPLING.DEROCERAS, SAMPLING.HERB, SAMPLING.SLUG)
rm(INTERACTIONS, INTERACTIONS.ALL)
```

# 04.1 - SLUGS TRANSECTS / MODELS

```{r 04.1 NEW SLUGS TRANSECTS DATA FORMATING NEGATIVE BINOMIAL, fig.width = 10, warning = FALSE, message = FALSE}

# 04.11 MODEL SELECTION
#######################

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "AIC" = 9999,
  "d.AIC" = 9999)

# THREE COVARIABLES
#------------------  

# mod3.1
mod3.1 <- glmer.nb(sqrt(SLUG) ~ LIGHT * DISTANCE * SPECIES + TEMP + AREA + (1|DISTANCE), data = SAMPLING)
summary(mod3.1)

Model <- "mod3.1"
Variable <- "SLUG ~ LIGHT * DISTANCE * SPECIES + TEMP + AREA + (1 SAMPLING)"
AIC <- AIC(mod3.1)  
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.1)

# mod3.2
mod3.2 <- glmer.nb(sqrt(SLUG) ~ LIGHT * DISTANCE + SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod3.2"
Variable <- "SLUG ~ LIGHT * DISTANCE + SPECIES + TEMP + AREA + (1 SAMPLING)"
AIC <- AIC(mod3.2)  
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.2)

# mod3.3
mod3.3 <- glmer.nb(sqrt(SLUG) ~ LIGHT + DISTANCE * SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod3.3"
Variable <- "SLUG ~ LIGHT + DISTANCE * SPECIES + TEMP + AREA + (1 SAMPLING)"
AIC <- AIC(mod3.3)  
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.3)  

# mod3.4
mod3.4 <- glmer.nb(sqrt(SLUG) ~ LIGHT + DISTANCE + SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod3.4"
Variable <- "SLUG ~ LIGHT + DISTANCE + SPECIES + RAIN + AREA + (1 SAMPLING)"
AIC <- AIC(mod3.4)  
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod3.4)  

# TWO COVARIABLES
#----------------

# mod2.1
mod2.1 <- glmer.nb(sqrt(SLUG) ~ LIGHT * DISTANCE + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod2.1"
Variable <- "SLUG ~ LIGHT * DISTANCE + AREA + (1 SAMPLING)"
AIC <- AIC(mod2.1)  
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1)

# mod2.2
mod2.2 <- glmer.nb(sqrt(SLUG) ~ LIGHT + DISTANCE + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod2.2"
Variable <- "SLUG ~ LIGHT + DISTANCE + AREA + (1 SAMPLING)"
AIC <- AIC(mod2.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2)

# ONE VARIABLE
#-------------

# mod1.1
mod1.1 <- glmer.nb(sqrt(SLUG) ~ LIGHT + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod1.1"
Variable <- "SLUG ~ LIGHT + AREA + (1 SAMPLING)"
AIC <- AIC(mod1.1)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1)

# mod1.2
mod1.2 <- glmer.nb(sqrt(SLUG) ~ DISTANCE + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod1.2"
Variable <- "SLUG ~ DISTANCE + AREA + (1 SAMPLING)"
AIC <- AIC(mod1.2)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.2)

# ZERO VARIABLE
#--------------

# mod0
mod0 <- glmer.nb(sqrt(SLUG) ~ AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

Model <- "mod0"
Variable <- "SLUG ~ AREA + (1 SAMPLING)"
AIC <- AIC(mod0)
dAIC <- NA

list <- c(Model, Variable, AIC, dAIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod0)

#-----------------------------------------------------------------------------------------------------------

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(j in (1:nrow(AIC.TABLE))){
  
  AIC.TABLE$d.AIC[j] <- round(AIC.TABLE$AIC[j] - AIC.min, 2)
  
}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

#-------------------------------------------------------------------------------------------------------------
  
# BEST MODEL
#-----------

# ADD SPECIES VARIABLES
mod04.1 <- glmer.nb(sqrt(SLUG) ~ LIGHT * DISTANCE * SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING), data = SAMPLING)

res <- residuals(mod04.1)
qqnorm(res)
qqline(res)

mod04.1.tbl <- tbl_regression(mod04.1, intercept = T) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**SLUG ~ LIGHT * DISTANCE * SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(mod04.1.tbl)
# print(mod04.1.tbl)

# REMOVE
rm(mod04.1.tbl)
rm(AIC.TABLE, AIC, AIC.min, dAIC, list, Model, Variable, j, res)

##############################################################################################################

# 04.12 PLOT EFFECT SIZE - ONLY CLOSE
#####################################

mod04.1 <- glmer.nb(sqrt(SLUG) ~ LIGHT * SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING), data = SAMPLING[SAMPLING$DISTANCE == "CLOSE",])

# POWER SIMULATION
#-----------------

nsim <- 10000

SAMPLING$SPECIES <- as.factor(SAMPLING$SPECIES)
n.level <- nlevels(SAMPLING$SPECIES)
SPECIES.LS <- levels(SAMPLING$SPECIES)

# SIMULATION
bsim <- sim(mod04.1, n.sim = nsim)

# CALCULATE EFFECT SIZE
#----------------------

# EMPTY MATRIX
effmat <- matrix(ncol = nsim, nrow = n.level)
effmat[1,] <- bsim@fixef[, "LIGHTLIGHT"]

# FOR LOOP
for(i in (2:n.level)){

  # i <- 2
  # print(i)

  effmat[i,] <- bsim@fixef[, "LIGHTLIGHT"] +
                bsim@fixef[, paste0("LIGHTLIGHT:SPECIES", levels(SAMPLING$SPECIES)[i])]
}

# CHECK COEFFICIENTS
CI <- apply(effmat, 1, quantile, probs = c(0.025, 0.5, 0.975))
CI <- cbind(c(0.025, 0.5, 0.975), CI)

rm(mod04.1, bsim, effmat, i, nsim)

# MERGE MATRIX
#--------------
colnames(CI) <- c("Level", c("A. lusitanicus", "D. reticulatum"))
rownames(CI) <- NULL

CI <- as.data.frame(CI)
CI$Level <- as.numeric(CI$Level)

CI <- CI[order(CI$Level),]

# FORMAT CI
#----------

CI.coef <- data.frame(
  "i.SPECIES" = 9999,
  "i.2.5" = 9999,
  "i.50" = 9999,
  "i.97.5" = 9999,
  "i.significant" = 9999)

for(i in SPECIES.LS){ 
  
  i.CI.coef <- CI.coef[1,]
  i.2.5 <- CI[1, i]
  i.50 <- CI[2, i]
  i.97.5 <- CI[3, i]
  
  i.SPECIES <- i
  i.significant <- 0

  i.CI.coef <- cbind(i.SPECIES, i.2.5, i.50, i.97.5, i.significant)
  CI.coef <- rbind(CI.coef, i.CI.coef)

}

# REMOVE FIRST LINE FULL OF NA's
CI.coef <- CI.coef[-1,]

# FORMAT
CI.coef$i.2.5 <- as.numeric(CI.coef$i.2.5)
CI.coef$i.50 <- as.numeric(CI.coef$i.50)
CI.coef$i.97.5 <- as.numeric(CI.coef$i.97.5)

# SIGNIFICANT IF IT TOUCH THE LINE
for(i in (1:nrow(CI.coef))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    {(CI.coef$i.97.5[i] < 0 & CI.coef$i.2.5[i] < 0) | 
     (CI.coef$i.97.5[i] > 0 & CI.coef$i.2.5[i] > 0)},
    
    # IF YES
    CI.coef$i.significant[i] <- 1,
   
    # IF NO
    CI.coef$i.significant[i] <- 0)  
}

rm(CI, i.CI.coef)
rm(i, i.2.5, i.50, i.97.5, i.SPECIES, n.level, i.significant)

# SEGMENT PLOT
#-------------

g <- rasterGrob(matrix(c("grey90"), nrow = 1), width = unit(1,"npc"), height = unit(1,"npc"), interpolate = TRUE)

# PLOT
`04.12_SLUGS_CI_CLOSE` <- ggplot() +
  
  annotation_custom(g, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  geom_hline(
    yintercept = 0,
    linetype = "dashed") + 
  geom_linerange(
    data = CI.coef,
    aes(
      x = i.SPECIES,
      ymin = i.2.5,
      ymax = i.97.5),
      linewidth = 4,
      alpha = 0.5,
      position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef,
    aes(x = i.SPECIES,
    y = i.50),
    shape = 18,
    size = 8,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.significant == "0",],
    aes(
      x = i.SPECIES,
      y = i.50),
      color = "white",
      shape = 18,
      size = 6,
      position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_classic() +
  labs(
    y = "Estimate",
    x = "Species",
    title = "Close (< 5 m)") +
  # scale_y_continuous(
  #   limits = c(-2.5, 2.5)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.line = element_blank(),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 10))

plot(`04.12_SLUGS_CI_CLOSE`)
#--------------------------------------------------------------------------------------------------------------

# 04.13 PLOT EFFECT SIZE - ONLY FAR
#####################################

mod04.1 <- glmer.nb(sqrt(SLUG) ~ LIGHT * SPECIES + TEMP + AREA + (1|PAIRS.SAMPLING), data = SAMPLING[SAMPLING$DISTANCE == "FAR",])

# POWER SIMULATION
#-----------------

nsim <- 10000

SAMPLING$SPECIES <- as.factor(SAMPLING$SPECIES)
n.level <- nlevels(SAMPLING$SPECIES)
SPECIES.LS <- levels(SAMPLING$SPECIES)

# SIMULATION
bsim <- sim(mod04.1, n.sim = nsim)

# CALCULATE EFFECT SIZE
#----------------------

# EMPTY MATRIX
effmat <- matrix(ncol = nsim, nrow = n.level)
effmat[1,] <- bsim@fixef[, "LIGHTLIGHT"]

# FOR LOOP
for(i in (2:n.level)){

  # i <- 2
  # print(i)

  effmat[i,] <- bsim@fixef[, "LIGHTLIGHT"] +
                bsim@fixef[, paste0("LIGHTLIGHT:SPECIES", levels(SAMPLING$SPECIES)[i])]
}

# CHECK COEFFICIENTS
CI <- apply(effmat, 1, quantile, probs = c(0.025, 0.5, 0.975))
CI <- cbind(c(0.025, 0.5, 0.975), CI)

rm(mod04.1, bsim, effmat, i, nsim)

# MERGE MATRIX
#--------------
colnames(CI) <- c("Level", c("A. lusitanicus", "D. reticulatum"))
rownames(CI) <- NULL

CI <- as.data.frame(CI)
CI$Level <- as.numeric(CI$Level)

CI <- CI[order(CI$Level),]

# FORMAT CI
#----------

CI.coef <- data.frame(
  "i.SPECIES" = 9999,
  "i.2.5" = 9999,
  "i.50" = 9999,
  "i.97.5" = 9999,
  "i.significant" = 9999)

for(i in SPECIES.LS){ 
  
  i.CI.coef <- CI.coef[1,]
  i.2.5 <- CI[1, i]
  i.50 <- CI[2, i]
  i.97.5 <- CI[3, i]
  
  i.SPECIES <- i
  i.significant <- 0

  i.CI.coef <- cbind(i.SPECIES, i.2.5, i.50, i.97.5, i.significant)
  CI.coef <- rbind(CI.coef, i.CI.coef)

}

# REMOVE FIRST LINE FULL OF NA's
CI.coef <- CI.coef[-1,]

# FORMAT
CI.coef$i.2.5 <- as.numeric(CI.coef$i.2.5)
CI.coef$i.50 <- as.numeric(CI.coef$i.50)
CI.coef$i.97.5 <- as.numeric(CI.coef$i.97.5)

# SIGNIFICANT IF IT TOUCH THE LINE
for(i in (1:nrow(CI.coef))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    {(CI.coef$i.97.5[i] < 0 & CI.coef$i.2.5[i] < 0) | 
     (CI.coef$i.97.5[i] > 0 & CI.coef$i.2.5[i] > 0)},
    
    # IF YES
    CI.coef$i.significant[i] <- 1,
   
    # IF NO
    CI.coef$i.significant[i] <- 0)  
}

rm(CI, i.CI.coef)
rm(i, i.2.5, i.50, i.97.5, i.SPECIES, n.level, i.significant)

# SEGMENT PLOT
#-------------
g <- rasterGrob(matrix(c("grey40"), nrow = 1), width = unit(1,"npc"), height = unit(1,"npc"), interpolate = TRUE)

# PLOT
`04.13_SLUGS_CI_FAR` <- ggplot() +
  
  annotation_custom(g, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  geom_hline(
    yintercept = 0,
    linetype = "dashed") + 
  geom_linerange(
    data = CI.coef,
    aes(
      x = i.SPECIES,
      ymin = i.2.5,
      ymax = i.97.5),
      linewidth = 4,
      alpha = 0.5,
      position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef,
    aes(x = i.SPECIES,
    y = i.50),
    shape = 18,
    size = 8,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.significant == "0",],
    aes(
      x = i.SPECIES,
      y = i.50),
      color = "white",
      shape = 18,
      size = 6,
      position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_classic() +
  labs(
    y = "Estimate",
    x = "SPECIES",
    title = "Far (> 5 m)") +
  # scale_y_continuous(
  #   limits = c(-1.5, 1.5)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.line = element_blank(),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_blank(),
    axis.text.y = element_blank())

#--------------------------------------------------------------------------------------------------------------

# FINAL PLOT
#-----------

`04.1_SLUGS_CI` <- grid.arrange(`04.12_SLUGS_CI_CLOSE`, 
                                `04.13_SLUGS_CI_FAR`, nrow = 1, widths = c(1.2, 1))

# FINAL REMOVE
##############
rm(SAMPLING, CI.coef, SPECIES.LS)
rm(`04.1_SLUGS_CI`, `04.12_SLUGS_CI_CLOSE`, `04.13_SLUGS_CI_FAR`, g)

```

# 05.0 - HERBIVORY IN SITU / DATA FORMATING & EXPLORATORY PLOTS

```{r 05.0 HERBIVORY IN SITU DATA FORMATING AND EXPLORATORY PLOTS, fig.width = 10, warning = FALSE, message = FALSE}

# FORMAT
########

# TRANSFORM % INTO NUMERIC
#-------------------------

col.names <- c("M_LEA_DAM0", "M_LEA_DAM1", "M_LEA_DAM2", "M_LEA_DAM3", "M_LEA_DAM4",
             "M_LEA_DAM5", "M_LEA_DAM6", "M_LEA_DAM7", "M_LEA_DAM8", "M_LEA_DAM9",
             "M_FLO_DAM1", "M_FLO_DAM2", "M_FLO_DAM3", "M_FLO_DAM4", "M_FLO_DAM5")

for(i in col.names){
  
  # i <- "B_LEA_DAM6"
  
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "1%", "0.01")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "10%", "0.1")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "15%", "0.15")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "20%", "0.2")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "25%", "0.25")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "30%", "0.3")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "40%", "0.4")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "50%", "0.5")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "60%", "0.6")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "70%", "0.7")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "80%", "0.8")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "90%", "0.9")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "100%", "1")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "0%", "0")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "5%", "0.05")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], "NOT MEAS", "NA")
  TRAITS[,i] <- str_replace_all(TRAITS[,i], " ", "NA")

  TRAITS[,i] <- as.numeric(TRAITS[,i])

}

rm(col.names)

# ADD LIGHT TREATMENT
#--------------------

TRAITS$S_LIGHT_TRMT <- NA

for(i in (1:nrow(TRAITS))){
  
  i.S_STU.SI <- TRAITS$S_STU.SI[i]
  ifelse(
    
    # STATEMENT
    i.S_STU.SI %in% LIT.SITE,
    
    # IF YES
    TRAITS$S_LIGHT_TRMT[i] <- "LIT",
    
    # IF NO
    TRAITS$S_LIGHT_TRMT[i] <- "DARK")}

rm(i.S_STU.SI, i)
#-------------------------------------------------------------------------------------------------------------

# CALCULATE SEVERITY, PROPORTION & ABSOLUTE NUMBER OF EATEN LEAVE FOR EACH POT
##############################################################################

# CREATE EMPTY VARIABLES
TRAITS$LEA.PROP <- NA
TRAITS$LEA.SEVER <- NA
TRAITS$LEA.ABS <- NA
TRAITS$LEA.PRESENT <- NA

TRAITS$FLO.PROP <- NA
TRAITS$FLO.SEVER <- NA
TRAITS$FLO.ABS <- NA
TRAITS$FLO.PRESENT <- NA

THRESHOLD <- 0

# FOR LOOP
for(i in (1:nrow(TRAITS))){
  
  # i <- 368
  # print(TRAITS$P_PL_LABEL[i])
  
  i.TRAITS <- TRAITS[i,]
  
  # LEAVE DAMAGES PROPORTION
  #-------------------------
  zero.ls <- c(i.TRAITS$M_LEA_DAM0, i.TRAITS$M_LEA_DAM1, i.TRAITS$M_LEA_DAM2, i.TRAITS$M_LEA_DAM3, i.TRAITS$M_LEA_DAM4,
               i.TRAITS$M_LEA_DAM5, i.TRAITS$M_LEA_DAM6, i.TRAITS$M_LEA_DAM7, i.TRAITS$M_LEA_DAM8, i.TRAITS$M_LEA_DAM9)
  
  zero.ls.n <- length(zero.ls[!is.na(zero.ls)])
  TRAITS$LEA.PRESENT[i] <- 10 - length(zero.ls[is.na(zero.ls)])

  TRAITS$LEA.PROP[i] <- 1 - ((length(zero.ls[zero.ls <= THRESHOLD & !is.na(zero.ls)])) / zero.ls.n)
  
  # HERBIVORY ABSOLUTE
  #-------------------
  damaged.ls.n <- length(zero.ls[which(zero.ls > THRESHOLD)])
  TRAITS$LEA.ABS[i] <- damaged.ls.n

  # LEAVE SEVERITY
  #---------------
  ifelse(
    
    # ARGUMENT
    mean(zero.ls, na.rm = T) == 0,
    
    # IF YES
    TRAITS$LEA.SEVER[i] <- 0,
    
    # IF NO
    TRAITS$LEA.SEVER[i] <- mean(zero.ls[which(zero.ls >= THRESHOLD)], na.rm = T)
    )
    
  # FLORIVORY PROPORTION
  #---------------------
  zero.ls <- c(i.TRAITS$M_FLO_DAM1, i.TRAITS$M_FLO_DAM2, i.TRAITS$M_FLO_DAM3, i.TRAITS$M_FLO_DAM4, i.TRAITS$M_FLO_DAM5)
  zero.ls.n <- length(zero.ls[!is.na(zero.ls)])
  TRAITS$FLO.PRESENT[i] <- 5 - length(zero.ls[is.na(zero.ls)])
  
  TRAITS$FLO.PROP[i] <- round(1 - (length(which(zero.ls == 0))) / zero.ls.n, 3)

  # FLORIVORY ABSOLUTE
  #-------------------
  damaged.ls.n <- length(zero.ls[which(zero.ls > 0)])
  TRAITS$FLO.ABS[i] <- damaged.ls.n
  
  # FLORIVORY SEVERITY
  #-------------------
  ifelse(
    
    # ARGUMENT
    mean(zero.ls, na.rm = T) == 0,
    
    # IF YES
    TRAITS$FLO.SEVER[i] <- 0,
    
    # IF NO
    TRAITS$FLO.SEVER[i] <- mean(zero.ls[zero.ls != 0], na.rm = T))

}

TRAITS$LEA.SEVER <- as.numeric(round(TRAITS$LEA.SEVER, 2))
TRAITS$LEA.PROP <- as.numeric(TRAITS$LEA.PROP)
TRAITS$FLO.SEVER <- as.numeric(round(TRAITS$FLO.SEVER, 2))
TRAITS$FLO.PROP <- as.numeric(TRAITS$FLO.PROP)

rm(i.TRAITS, damaged.ls.n, i, zero.ls, zero.ls.n, THRESHOLD)

#-------------------------------------------------------------------------------------------------------------

DAMAGE <- data.frame(
    
    SPECIES = NA,
    LABEL = NA,
    DATE = NA,
    STU.SI = NA,
    TREA_LIGHT = NA,
    LUX = NA,
    LAMP_DIST = NA,
    TYPE = NA,
    DAMAGES = NA)

# FOR LOOP
#----------
for(i in (1:nrow(TRAITS))){
  
  # i <- 45
  # print(i)
  
  i.TRAITS <- TRAITS[i,]
  i.LABEL <- i.TRAITS$P_PL_LABEL
  i.LABEL.short <- as.numeric(str_sub(i.LABEL, start = -4))

  # EMPTY DATA FRAME WITH 10 ROWS
  i.DAMAGE <- DAMAGE[1,]
  i.DAMAGE <- rbind(i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE,
                    i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE, i.DAMAGE)

  # FILL SAMPLING INFOS
  #--------------------
  i.DAMAGE$SPECIES <- i.TRAITS$P_PLANT_SP
  i.DAMAGE$LABEL <- i.LABEL
  i.DAMAGE$DATE <- i.TRAITS$S_DATE
  i.DAMAGE$STU.SI <- i.TRAITS$S_STU.SI 
  i.DAMAGE$TREA_LIGHT <- i.TRAITS$S_LIGHT_TRMT
  i.DAMAGE$LUX <- i.TRAITS$LUX
  i.DAMAGE$LAMP_DIST <- i.TRAITS$LAMP_DIST

  
  # FILL DAMAGES
  #-------------
  i.DAMAGES <- c(i.TRAITS$M_LEA_DAM0, i.TRAITS$M_LEA_DAM1, i.TRAITS$M_LEA_DAM2, i.TRAITS$M_LEA_DAM3, i.TRAITS$M_LEA_DAM4,
                 i.TRAITS$M_LEA_DAM5, i.TRAITS$M_LEA_DAM6, i.TRAITS$M_LEA_DAM7, i.TRAITS$M_LEA_DAM8, i.TRAITS$M_LEA_DAM9, 
                 i.TRAITS$M_FLO_DAM1, i.TRAITS$M_FLO_DAM2, i.TRAITS$M_FLO_DAM3, i.TRAITS$M_FLO_DAM4, i.TRAITS$M_FLO_DAM5)
  
  i.DAMAGE$TYPE <- c(rep("LEAVE", 10), rep("FLOWER", 5))
  i.DAMAGE$DAMAGES <- i.DAMAGES
  
  # MERGE
  DAMAGE <- rbind(DAMAGE, i.DAMAGE)
  
}

rm(i.DAMAGE, i.DAMAGES, i.TRAITS)
rm(i, i.LABEL, i.LABEL.short)

# CLEAN
#------

# Remove first line full of NA's 
DAMAGE <- DAMAGE[-1,] # 8160

# Remove NA's
DAMAGE <- DAMAGE[!is.na(DAMAGE$DAMAGES),] # 6192

##############################################################################################################¨

# VISUALIZE DATA
################

# COLOR PALETTE
#--------------
# COLOR PALETTE
COLOR.PALETTE <- c(wes_palettes$Cavalcanti1[5], # Centaurea jacea
                   wes_palettes$Darjeeling1[3], # Leucanthemum Vulgare
                   wes_palettes$IsleofDogs1[1]) # Malva moschata
                   
# LIGHT TREATMENT
#----------------
`05.0_LIGHT_TREATMENT.barplot` <- ggplot(
    data = TRAITS,
    aes(
      x = P_PLANT_SP,
      fill = P_PLANT_SP,
      pattern = S_LIGHT_TRMT),
    color = "blank") +
  geom_histogram_pattern(
    stat = "count",
    position = position_dodge(preserve = "single"),
    color = "white",
    pattern_fill = "white",
    pattern_angle = 45,
    pattern_density = 0.25,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  scale_pattern_manual(
    values = c(
    LIT   = "stripe", DARK  = "none")) +
  scale_fill_manual(
    values = COLOR.PALETTE) +
  theme_classic() +
  labs(
    x = "Plant species",
    y = "Measured individuals",
    title = "Number of individuals",
    pattern = "Light Treatment") +
  guides(
    fill = "none",
    pattern = guide_legend(ncol = 2, byrow = TRUE)) +
  theme(
    plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
    legend.position = c(0.8, 0.9),
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`05.0_LIGHT_TREATMENT.barplot`)

# SAVE
#-----
# ggsave(filename = "05.0_LIGHT_TREATMENT.barplot.jpeg",
#          plot = `05.0_LIGHT_TREATMENT.barplot`, path = HOME,
#          height = 16, width = 20, units = "cm")

rm(`05.0_LIGHT_TREATMENT.barplot`)

#-------------------------------------------------------------------------------------------------------------

# SAVE
#-----

DATADIR <- "C:/Users/vgrog/OneDrive/00_AGROSCOPE - ALAN PROJECT/06_ANALYSIS/2023/01_ALAN x HERBIVORY/OUTPUT/"
write.csv(DAMAGE, paste0(DATADIR, "DAMAGE.csv"))
rm(DATADIR)

```

# 05.1 - HERBIVORY IN SITU / HERBIVORY

```{r 05.1 HERBIVORY IN SITU HERBIVORY, fig.width = 10, warning = FALSE, message = FALSE}

# 05.11 NUMBER OF EATEN LEAVES
##############################

COLOR.PALETTE <- c(wes_palettes$Cavalcanti1[5], # Centaurea jacea
                   wes_palettes$Darjeeling1[3], # Leucanthemum Vulgare
                   wes_palettes$IsleofDogs1[1]) # Malva moschata

# SUBSET
SUBSET <- TRAITS

# PLOT
`05.11_PROP_LEA` <- ggplot(data = SUBSET, 
    aes(
      x = LEA.ABS,
      y = P_PLANT_SP,
      fill = P_PLANT_SP,
      pattern = S_LIGHT_TRMT)) +
  geom_boxplot_pattern(color = "black",
    pattern_fill = "white",
    pattern_angle = 45,
    pattern_density = 0.5,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(alpha = 0.15) +
  scale_pattern_manual(
    values = c("LIT" = "stripe", "DARK"  = "none"),
    name = "Light treatment",
    labels = c("Dark", "Light")) +                              
  scale_fill_manual(values = COLOR.PALETTE) +
  theme_minimal() +
  guides(fill = "none") +
  labs(
    title = "Number of damaged leaves within the 10 lowest",
    x = "Eaten leaves",
    y = "Species") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.position = "right",
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`05.11_PROP_LEA`)

# SAVE
# ggsave(filename = "05.11_PROP_LEA.jpeg",
#          plot = `05.11_PROP_LEA`, path = HOME,
#          height = 16, width = 20, units = "cm")

rm(`05.11_PROP_LEA`)

#-------------------------------------------------------------------------------------------------------------

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "anova.p" = 9999,
  "anova.dAIC" = 9999,
  "AIC" = 9999,
  "BIC" = 9999)

# mod2.1 - with interactions
mod2.1.light <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ S_LIGHT_TRMT * P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)
mod2.1 <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)

Model <- "mod2.1"
Variable <- "S_LIGHT_TRMT * P_PLANT_SP"

anova <- anova(mod2.1, mod2.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1, mod2.1.light)

# mod2.2 - without interactions
mod2.2.light <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ S_LIGHT_TRMT + P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)
mod2.2 <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)

Model <- "mod2.2"
Variable <- "S_LIGHT_TRMT + P_PLANT_SP"

anova <- anova(mod2.2, mod2.2.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2, mod2.2.light)

# mod1.1 - without species
mod1.1.light <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ S_LIGHT_TRMT + (1|S_STU.SI), data = SUBSET, family = binomial)
mod1.1 <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ 1 + (1|S_STU.SI), data = SUBSET, family = binomial)

Model <- "mod1.1"
Variable <- "S_LIGHT_TRMT"

anova <- anova(mod1.1, mod1.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1, mod1.1.light)

#-------------------------------------------------------------------------------------------------------------

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]
AIC.TABLE$d.AIC <- NA

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){
  
  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)
  
}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

# REMOVE
rm(AIC.TABLE, AIC, AIC.min, i, list, Model, Variable, anova.dAIC, anova.p, BIC, anova)
#-------------------------------------------------------------------------------------------------------------

# BEST MODEL
#-----------
mod05.11 <- glmer(cbind(LEA.ABS, LEA.PRESENT - LEA.ABS) ~ S_LIGHT_TRMT * P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)
qqnorm(residuals(mod05.11))
qqline(residuals(mod05.11))

mod05.11.tbl <- tbl_regression(mod05.11, 
                              intercept = T,
                              pvalue_fun = ~ style_pvalue(.x, digits = 3),
                              estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**cbind(Eaten leaves, 10 - Eaten leaves) ~ Light * Plant Sp. + (1|Study site)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(mod05.11.tbl)
# print(mod05.11.tbl)

# SAVE
# gtsave(as_gt(mod05.11.tbl),
#        file = file.path(paste0(HOME,"/mod05.11.tbl.png")))

# REMOVE
rm(mod05.11.tbl)

#-------------------------------------------------------------------------------------------------------------

# POWER SIMULATION
#-----------------

nsim <- 10000

SUBSET$P_PLANT_SP <- as.factor(SUBSET$P_PLANT_SP)
n.level <- nlevels(SUBSET$P_PLANT_SP)
PLANT.LS <- levels(SUBSET$P_PLANT_SP)

# SIMULATION
bsim <- sim(mod05.11, n.sim = nsim)

# CALCULATE EFFECT SIZE
#----------------------

# EMPTY MATRIX
effmat <- matrix(ncol = nsim, nrow = n.level)
effmat[1,] <- bsim@fixef[, "S_LIGHT_TRMTLIT"]

# FOR LOOP
for(i in (2:n.level)){

  # i <- 2
  # print(i)

  effmat[i,] <- bsim@fixef[, "S_LIGHT_TRMTLIT"] +
                bsim@fixef[, paste0("S_LIGHT_TRMTLIT:P_PLANT_SP", levels(SUBSET$P_PLANT_SP)[i])]
}

# CHECK COEFFICIENTS
CI.HERB.ABS <- apply(effmat, 1, quantile, probs = c(0.05, 0.5, 0.95))
CI.HERB.ABS <- cbind(rep("HERB.ABS", 3), CI.HERB.ABS)
CI.HERB.ABS <- cbind(c(0.05, 0.5, 0.95), CI.HERB.ABS)

kable(CI.HERB.ABS)

rm(mod05.11, bsim, effmat, i, nsim)

#-------------------------------------------------------------------------------------------------------------

# MERGE MATRIX
#--------------
CI <- CI.HERB.ABS
colnames(CI) <- c("Level", "DAMAGES", PLANT.LS)
rownames(CI) <- NULL

CI <- as.data.frame(CI)
CI$Level <- as.numeric(CI$Level)

CI <- CI[order(CI$Level),]

# FORMAT CI
#----------

CI.coef <- data.frame(
  "i.damages" = 9999,
  "i.species" = 9999,
  "i.2.5" = 9999,
  "i.50" = 9999,
  "i.97.5" = 9999,
  "i.significant" = 9999)

for(i in PLANT.LS){ 
  
  # i <- "Malva moschata"
  
  i.CI.coef <- CI.coef[1,]
  i.2.5 <- CI[1, i]
  i.50 <- CI[2, i]
  i.97.5 <- CI[3, i]
  
  i.species <- i
  i.damages <- unique(CI$DAMAGES)
  
  i.significant <- 0

  i.CI.coef <- cbind(i.species, i.damages, i.2.5, i.50, i.97.5, i.significant)
  CI.coef <- rbind(CI.coef, i.CI.coef)

}

# REMOVE FIRST LINE FULL OF NA's
CI.coef <- CI.coef[-1,]

# FORMAT
CI.coef$i.2.5 <- as.numeric(CI.coef$i.2.5)
CI.coef$i.50 <- as.numeric(CI.coef$i.50)
CI.coef$i.97.5 <- as.numeric(CI.coef$i.97.5)

# SIGNIFICANT IF IT TOUCH THE LINE
for(i in (1:nrow(CI.coef))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    {(CI.coef$i.97.5[i] < 0 & CI.coef$i.2.5[i] < 0) | 
     (CI.coef$i.97.5[i] > 0 & CI.coef$i.2.5[i] > 0)},
    
    # IF YES
    CI.coef$i.significant[i] <- 1,
   
    # IF NO
    CI.coef$i.significant[i] <- 0)  
}

rm(CI, CI.HERB.ABS, i.CI.coef)
rm(i, i.2.5, i.50, i.97.5, i.damages, i.significant, i.species, PLANT.LS, n.level)

#-------------------------------------------------------------------------------------------------------------

# SEGMENT PLOT
#-------------

`05.11_CI.HERB.ABS` <- ggplot() +

  geom_hline(
    yintercept = 0,
    linetype = "dashed") + 
  geom_linerange(
    data = CI.coef[CI.coef$i.damages == "HERB.ABS",],
    aes(
      x = i.species,
      ymin = i.2.5,
      ymax = i.97.5,
      color = i.species),
      linewidth = 4,
      alpha = 0.5,
      position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "HERB.ABS",],
    aes(x = i.species,
    y = i.50,
    color = i.species),
    shape = 18,
    size = 8,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "HERB.ABS" & CI.coef$i.significant == "0",],
    aes(
      x = i.species,
      y = i.50),
      color = "white",
      shape = 18,
      size = 6,
      position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_classic() +
  labs(
    y = "Estimate",
    x = "Species",
    title = "Number of eaten leaves") +
  scale_colour_manual(
    values = COLOR.PALETTE) +
  scale_y_continuous(
    limits = c(-1.5, 1.5)) +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 10, face = "bold"),
    axis.title.y = element_blank(),
    axis.line = element_blank(),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(hjust = 0.5, size = 8, face = "bold"),
    axis.text.x = element_text(size = 8))

# plot(`05.11_CI.HERB.ABS`)

# SAVE
# ggsave(filename = paste0("05.11_CI.HERB.ABS.jpeg"),
#          plot = `05.11_CI.HERB.ABS`, path = HOME,
#          height = 8, width = 16, units = "cm")

rm(CI.coef)

##############################################################################################################

# 05.12 SEVERITY OF EATEN LEAVES
################################

# SUBSET
#-------
THRESHOLD <- 0

SUBSET <- DAMAGE # 6192
SUBSET <- SUBSET[SUBSET$DAMAGES > THRESHOLD ,] # 3533
SUBSET <- SUBSET[SUBSET$TYPE == "LEAVE" ,] # 3049

# PLOT
#-----
`05.12_SEV_LEA` <- ggplot(data = SUBSET, 
    aes(
      x = DAMAGES,
      y = SPECIES,
      fill = SPECIES,
      pattern = TREA_LIGHT)) +
  geom_boxplot_pattern(color = "black",
    pattern_fill = "white",
    pattern_angle = 45,
    pattern_density = 0.5,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(alpha = 0.05) +
  scale_pattern_manual(
    values = c("LIT" = "stripe", "DARK"  = "none"),
    name = "Light treatment",
    labels = c("Dark", "Light")) +  
  scale_fill_manual(
    values = COLOR.PALETTE) +
  theme_minimal() +
  guides(
    fill = "none") +
  labs(
    title = "Severity of damaged leaves",
    x = "Severity of damaged leaves [%]",
    y = "Species") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.position = "right",
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`05.12_SEV_LEA`)

# SAVE
# ggsave(filename = "05.12_SEV_LEA.jpeg",
#          plot = `05.12_SEV_LEA`, path = HOME,
#          height = 16, width = 20, units = "cm")

rm(`05.12_SEV_LEA`)

#-------------------------------------------------------------------------------------------------------------

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "anova.p" = 9999,
  "anova.dAIC" = 9999,
  "AIC" = 9999,
  "BIC" = 9999)

# mod2.1 - with interactions
mod2.1.light <- lmer(DAMAGES ~ TREA_LIGHT * SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)
mod2.1 <- lmer(DAMAGES ~ SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)

Model <- "mod2.1"
Variable <- "TREA_LIGHT * SPECIES"

anova <- anova(mod2.1, mod2.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1, mod2.1.light)

# mod2.2 - without interactions
mod2.2.light <- lmer(DAMAGES ~ TREA_LIGHT + SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)
mod2.2 <- lmer(DAMAGES ~ SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)

Model <- "mod2.2"
Variable <- "TREA_LIGHT + SPECIES"

anova <- anova(mod2.2, mod2.2.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2, mod2.2.light)

# mod1.1 - without species
mod1.1.light <- lmer(DAMAGES ~ TREA_LIGHT + (1|STU.SI) + (1|LABEL), data = SUBSET)
mod1.1 <- lmer(DAMAGES ~ 1 + (1|STU.SI) + (1|LABEL), data = SUBSET)

Model <- "mod1.1"
Variable <- "TREA_LIGHT"

anova <- anova(mod1.1, mod1.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1, mod1.1.light)

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]
AIC.TABLE$d.AIC <- NA

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){

  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)

}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

# REMOVE
rm(AIC.TABLE, AIC, AIC.min, i, list, Model, Variable, anova.dAIC, anova.p, BIC, anova)
#-------------------------------------------------------------------------------------------------------------

# BEST MODEL
#-----------
mod05.12 <- lmer(sqrt(DAMAGES) ~ TREA_LIGHT * SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)
qqnorm(residuals(mod05.12))
qqline(residuals(mod05.12))

mod05.12.tbl <- tbl_regression(mod05.12, 
                              intercept = T,
                              pvalue_fun = ~ style_pvalue(.x, digits = 3),
                              estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**Leaves damages severity ~ Light * Plant Sp. + (1|Study site) + (1|Label)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

# PRINT
knit_print(mod05.12.tbl)
# print(mod05.12.tbl)

# SAVE
# gtsave(as_gt(mod05.12.tbl),
#        file = file.path(paste0(HOME,"/mod05.12.tbl.png")))

# REMOVE
rm(mod05.12.tbl)

#-------------------------------------------------------------------------------------------------------------

# POWER SIMULATION
#-----------------

nsim <- 10000

SUBSET$SPECIES <- as.factor(SUBSET$SPECIES)
n.level <- nlevels(SUBSET$SPECIES)
PLANT.LS <- levels(SUBSET$SPECIES)

# SIMULATION
bsim <- sim(mod05.12, n.sim = nsim)

# CALCULATE EFFECT SIZE
#----------------------

# EMPTY MATRIX
effmat <- matrix(ncol = nsim, nrow = n.level)
effmat[1,] <- bsim@fixef[, "TREA_LIGHTLIT"]

# FOR LOOP
for(i in (2:n.level)){

  # i <- 2

  effmat[i,] <- bsim@fixef[, "TREA_LIGHTLIT"] +
                bsim@fixef[, paste0("TREA_LIGHTLIT:SPECIES", levels(SUBSET$SPECIES)[i])]
}

# CHECK COEFFICIENTS
CI.HERB.SEV <- apply(effmat, 1, quantile, probs = c(0.05, 0.5, 0.95))
CI.HERB.SEV <- cbind(rep("HERB.SEV", 3), CI.HERB.SEV)
CI.HERB.SEV <- cbind(c(0.05, 0.5, 0.95), CI.HERB.SEV)

kable(CI.HERB.SEV)

rm(mod05.12, bsim, effmat, i, nsim)

#-------------------------------------------------------------------------------------------------------------

# MERGE MATRIX
#--------------
CI <- CI.HERB.SEV
colnames(CI) <- c("Level", "DAMAGES", PLANT.LS)
rownames(CI) <- NULL

CI <- as.data.frame(CI)
CI$Level <- as.numeric(CI$Level)

CI <- CI[order(CI$Level),]

# FORMAT CI
#----------

CI.coef <- data.frame(
  "i.damages" = 9999,
  "i.species" = 9999,
  "i.2.5" = 9999,
  "i.50" = 9999,
  "i.97.5" = 9999,
  "i.significant" = 9999)

for(i in PLANT.LS){ 
  
  # i <- "Malva moschata"
  
  i.CI.coef <- CI.coef[1,]
  i.2.5 <- CI[1, i]
  i.50 <- CI[2, i]
  i.97.5 <- CI[3, i]
  
  i.species <- i
  i.damages <- unique(CI$DAMAGES)
  
  i.significant <- 0

  i.CI.coef <- cbind(i.species, i.damages, i.2.5, i.50, i.97.5, i.significant)
  CI.coef <- rbind(CI.coef, i.CI.coef)

}

# REMOVE FIRST LINE FULL OF NA's
CI.coef <- CI.coef[-1,]

# FORMAT
CI.coef$i.2.5 <- as.numeric(CI.coef$i.2.5)
CI.coef$i.50 <- as.numeric(CI.coef$i.50)
CI.coef$i.97.5 <- as.numeric(CI.coef$i.97.5)

# SIGNIFICANT IF IT TOUCH THE LINE
for(i in (1:nrow(CI.coef))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    {(CI.coef$i.97.5[i] < 0 & CI.coef$i.2.5[i] < 0) | 
     (CI.coef$i.97.5[i] > 0 & CI.coef$i.2.5[i] > 0)},
    
    # IF YES
    CI.coef$i.significant[i] <- 1,
   
    # IF NO
    CI.coef$i.significant[i] <- 0)  
}

rm(CI, CI.HERB.SEV, i.CI.coef)
rm(i, i.2.5, i.50, i.97.5, i.damages, i.significant, i.species, PLANT.LS, n.level)

#-------------------------------------------------------------------------------------------------------------

# SEGMENT PLOT
#-------------

`05.12_CI.HERB.SEV` <- ggplot() +

  geom_hline(
    yintercept = 0, 
    linetype = "dashed") + 
  geom_linerange(
    data = CI.coef[CI.coef$i.damages == "HERB.SEV",],
    aes(
      x = i.species,
      ymin = i.2.5,
      ymax = i.97.5,
      color = i.species),
    size = 4,
    alpha = 0.5,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "HERB.SEV",],
    aes(
      x = i.species,
      y = i.50,
      color = i.species),
      shape = 18,
      size = 8,
      position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "HERB.SEV" & CI.coef$i.significant == "0",],
    aes(
      x = i.species,
      y = i.50),
    color = "white",
    shape = 18,
    size = 6,
    position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_classic() +
  labs(
    y = "Estimate",
    x = "Species",
    title = "Severity of eaten leaves") +
  scale_colour_manual(values = COLOR.PALETTE) +
  scale_y_continuous(limits = c(-0.2, 0.2)) +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 10, face = "bold"),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.line = element_blank(),
    # axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5, face = "italic"),
    axis.title.x = element_text(hjust = 0.5, size = 8, face = "bold"),
    axis.text.x = element_text(size = 8))

# plot(`05.12_CI.HERB.SEV`)

# SAVE
# ggsave(filename = paste0("05.12_CI.HERB.SEV.jpeg"),
#          plot = `05.12_CI.HERB.SEV`, path = HOME,
#          height = 8, width = 16, units = "cm")

rm(CI.coef, THRESHOLD)

```

# 05.2 - HERBIVORY IN SITU / FLORIVORY

```{r 05.2 HERBIVORY IN SITU FLORIVORY, fig.width = 10, warning = FALSE, message = FALSE}

# 05.21 ABSOLUTE NUMBER OF EATEN FLOWERS
########################################

# SUBSET
SUBSET <- TRAITS

# PLOT
`05.21_ABS_FLO` <- ggplot(data = SUBSET, 
    aes(
      x = FLO.ABS,
      y = P_PLANT_SP,
      fill = P_PLANT_SP,
      pattern = S_LIGHT_TRMT)) +
  geom_boxplot_pattern(
    color = "black",
    pattern_fill = "white",
    pattern_angle = 45,
    pattern_density = 0.5,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(
    alpha = 0.15) +
  scale_pattern_manual(
    values = c("LIT" = "stripe", "DARK"  = "none"),
    name = "Light treatment",
    labels = c("Dark", "Light")) +    scale_fill_manual(values = COLOR.PALETTE) +
  theme_minimal() +
  guides(fill = "none") +
  labs(
    title = "Number of damaged flowers",
    x = "Eaten flowers",
    y = "Species") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.position = "right",
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`05.21_ABS_FLO`)

# # SAVE
# ggsave(filename = "05.21_ABS_FLO.jpeg",
#          plot = `05.21_ABS_FLO`, path = HOME,
#          height = 16, width = 20, units = "cm")

rm(`05.21_ABS_FLO`)

#-------------------------------------------------------------------------------------------------------------

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "anova.p" = 9999,
  "anova.dAIC" = 9999,
  "AIC" = 9999,
  "BIC" = 9999)

# mod2.1 - with interactions
mod2.1.light <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ S_LIGHT_TRMT * P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)
mod2.1 <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)

Model <- "mod2.1"
Variable <- "S_LIGHT_TRMT * P_PLANT_SP"

anova <- anova(mod2.1, mod2.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1, mod2.1.light)

# mod2.2 - without interactions
mod2.2.light <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ S_LIGHT_TRMT + P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)
mod2.2 <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)

Model <- "mod2.2"
Variable <- "S_LIGHT_TRMT + P_PLANT_SP"

anova <- anova(mod2.2, mod2.2.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2, mod2.2.light)

# mod1.1 - without species
mod1.1.light <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ S_LIGHT_TRMT + (1|S_STU.SI), data = SUBSET, family = binomial)
mod1.1 <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ 1 + (1|S_STU.SI), data = SUBSET, family = binomial)

Model <- "mod1.1"
Variable <- "S_LIGHT_TRMT"

anova <- anova(mod1.1, mod1.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1, mod1.1.light)

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]
AIC.TABLE$d.AIC <- NA

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){
  
  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)
  
}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

rm(AIC.TABLE, AIC, AIC.min, i, list, Model, Variable, anova.dAIC, anova.p, BIC, anova)
#-------------------------------------------------------------------------------------------------------------

# BEST MODEL
#-----------

# MODEL
mod05.21 <- glmer(cbind(FLO.ABS, FLO.PRESENT - FLO.ABS) ~ S_LIGHT_TRMT * P_PLANT_SP + (1|S_STU.SI), data = SUBSET, family = binomial)
qqnorm(residuals(mod05.21))
qqline(residuals(mod05.21))

# PRINT
mod05.21.tbl <- tbl_regression(mod05.21, 
                              intercept = T,
                              pvalue_fun = ~ style_pvalue(.x, digits = 3),
                              estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**Eaten flowers ~ Light * Plant Sp. + (1|Study site)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()
  
knit_print(mod05.21.tbl)
# print(mod05.21.tbl)

# SAVE
# gtsave(as_gt(mod05.21.tbl),
#        file = file.path(paste0(HOME,"/mod03.13.tbl.png")))

rm(mod05.21.tbl)

#-------------------------------------------------------------------------------------------------------------

# POWER SIMULATION
#-----------------

nsim <- 10000

SUBSET$P_PLANT_SP <- as.factor(SUBSET$P_PLANT_SP)
n.level <- nlevels(SUBSET$P_PLANT_SP)
PLANT.LS <- levels(SUBSET$P_PLANT_SP)

# SIMULATION
bsim <- sim(mod05.21, n.sim = nsim)

# CALCULATE EFFECT SIZE
#----------------------

# EMPTY MATRIX
effmat <- matrix(ncol = nsim, nrow = n.level)
effmat[1,] <- bsim@fixef[, "S_LIGHT_TRMTLIT"]

# FOR LOOP
for(i in (2:n.level)){

  # i <- 2
  print(i)

  effmat[i,] <- bsim@fixef[, "S_LIGHT_TRMTLIT"] +
                bsim@fixef[, paste0("S_LIGHT_TRMTLIT:P_PLANT_SP", levels(SUBSET$P_PLANT_SP)[i])]
}

# CHECK COEFFICIENTS
CI.FLO.ABS <- apply(effmat, 1, quantile, probs = c(0.05, 0.5, 0.95))
CI.FLO.ABS <- cbind(rep("FLO.ABS", 3), CI.FLO.ABS)
CI.FLO.ABS <- cbind(c(0.05, 0.5, 0.95), CI.FLO.ABS)

kable(CI.FLO.ABS)

rm(mod05.21, bsim, effmat, i, nsim)

#-------------------------------------------------------------------------------------------------------------

# MERGE MATRIX
#--------------
CI <- CI.FLO.ABS
colnames(CI) <- c("Level", "DAMAGES", PLANT.LS)
rownames(CI) <- NULL

CI <- as.data.frame(CI)
CI$Level <- as.numeric(CI$Level)

CI <- CI[order(CI$Level),]

# FORMAT CI
#----------

CI.coef <- data.frame(
  "i.damages" = 9999,
  "i.species" = 9999,
  "i.2.5" = 9999,
  "i.50" = 9999,
  "i.97.5" = 9999,
  "i.significant" = 9999)

for(i in PLANT.LS){ 
  
  # i <- "Malva moschata"
  
  i.CI.coef <- CI.coef[1,]
  i.2.5 <- CI[1, i]
  i.50 <- CI[2, i]
  i.97.5 <- CI[3, i]
  
  i.species <- i
  i.damages <- unique(CI$DAMAGES)
  
  i.significant <- 0

  i.CI.coef <- cbind(i.species, i.damages, i.2.5, i.50, i.97.5, i.significant)
  CI.coef <- rbind(CI.coef, i.CI.coef)

}

# REMOVE FIRST LINE FULL OF NA's
CI.coef <- CI.coef[-1,]

# FORMAT
CI.coef$i.2.5 <- as.numeric(CI.coef$i.2.5)
CI.coef$i.50 <- as.numeric(CI.coef$i.50)
CI.coef$i.97.5 <- as.numeric(CI.coef$i.97.5)

# SIGNIFICANT IF IT TOUCH THE LINE
for(i in (1:nrow(CI.coef))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    {(CI.coef$i.97.5[i] < 0 & CI.coef$i.2.5[i] < 0) | 
     (CI.coef$i.97.5[i] > 0 & CI.coef$i.2.5[i] > 0)},
    
    # IF YES
    CI.coef$i.significant[i] <- 1,
   
    # IF NO
    CI.coef$i.significant[i] <- 0)  
}

rm(CI, CI.FLO.ABS, i.CI.coef)
rm(i, i.2.5, i.50, i.97.5, i.damages, i.significant, i.species, PLANT.LS, n.level)

#-------------------------------------------------------------------------------------------------------------

# SEGMENT PLOT
#-------------

`05.21_CI.FLO.ABS` <- ggplot() +
  
  geom_hline(
    yintercept = 0,
    linetype = "dashed") + 
  geom_linerange(
    data = CI.coef[CI.coef$i.damages == "FLO.ABS",],
    aes(
      x = i.species,
      ymin = i.2.5,
      ymax = i.97.5,
      color = i.species),
    linewidth = 4,
    alpha = 0.5,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "FLO.ABS",],
    aes(
      x = i.species,
      y = i.50,
      color = i.species),
    shape = 18,
    size = 8,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "FLO.ABS" & CI.coef$i.significant == "0",],
    aes(
      x = i.species,
      y = i.50),
    color = "white",
    shape = 18,
    size = 6,
    position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_classic() +
  labs(
    y = "Estimate",
    x = "Species",
    title = "Number of eaten flowers") +
  scale_colour_manual(
    values = COLOR.PALETTE) +
  scale_y_continuous(
    limits = c(-1.5, 1.5)) +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 10, face = "bold"),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.line = element_blank(),
    # axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5, face = "italic"),
    axis.title.x = element_text(size = 8, face = "bold"),
    axis.text.x = element_text(size = 8))

# plot(`05.21_CI.FLO.ABS`)

# ggsave(filename = paste0("05.21_CI.FLO.ABS.jpeg"),
#          plot = `05.21_CI.FLO.ABS`, path = HOME,
#          height = 8, width = 16, units = "cm")

rm(CI.coef)

##############################################################################################################

# 05.22 SEVERITY OF EATEN FLOWERS
#################################

# SUBSET
#-------
THRESHOLD <- 0

SUBSET <- DAMAGE #6192
SUBSET <- SUBSET[SUBSET$DAMAGES > THRESHOLD ,] # 3533
SUBSET <- SUBSET[SUBSET$TYPE == "FLOWER" ,] # 484

# PLOT
#-----
`05.22_SEV_FLO` <- ggplot(
  data = SUBSET, 
  aes(
    x = DAMAGES,
    y = SPECIES,
    fill = SPECIES,
    pattern = TREA_LIGHT)) +
  geom_boxplot_pattern(
    color = "black",
    pattern_fill = "white",
    pattern_angle = 45,
    pattern_density = 0.5,
    pattern_color = NA,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6) +
  geom_jitter(
    alpha = 0.3) +
  scale_pattern_manual(
    values = c("LIT" = "stripe", "DARK"  = "none"),
    name = "Light treatment",
    labels = c("Dark", "Light")) +       
  scale_fill_manual(
    values = COLOR.PALETTE) +
  theme_minimal() +
  guides(
    fill = "none") +
  labs(
    title = "Severity of damaged flowers",
    x = "Severity of damaged flowers [%]",
    y = "Species") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.position = "right",
    legend.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 12))

plot(`05.22_SEV_FLO`)

# ggsave(filename = "05.22_SEV_FLO.jpeg",
#          plot = `05.22_SEV_FLO`, path = HOME,
#          height = 16, width = 20, units = "cm")

rm(`05.22_SEV_FLO`)

#-------------------------------------------------------------------------------------------------------------

# MODEL SELECTION
#----------------

# Create an empty df
AIC.TABLE <- data.frame(
  "Model" = 9999,
  "Variable" = 9999,
  "anova.p" = 9999,
  "anova.dAIC" = 9999,
  "AIC" = 9999,
  "BIC" = 9999)

# mod2.1 - with interactions
mod2.1.light <- lmer(DAMAGES ~ TREA_LIGHT * SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)
mod2.1 <- lmer(DAMAGES ~ SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)

Model <- "mod2.1"
Variable <- "TREA_LIGHT * SPECIES"

anova <- anova(mod2.1, mod2.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.1, mod2.1.light)

# mod2.2 - without interactions
mod2.2.light <- lmer(DAMAGES ~ TREA_LIGHT + SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)
mod2.2 <- lmer(DAMAGES ~ SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)

Model <- "mod2.2"
Variable <- "TREA_LIGHT + SPECIES"

anova <- anova(mod2.2, mod2.2.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod2.2, mod2.2.light)

# mod1.1 - without species
mod1.1.light <- lmer(DAMAGES ~ TREA_LIGHT + (1|STU.SI) + (1|LABEL), data = SUBSET)
mod1.1 <- lmer(DAMAGES ~ 1 + (1|STU.SI) + (1|LABEL), data = SUBSET)

Model <- "mod1.1"
Variable <- "TREA_LIGHT"

anova <- anova(mod1.1, mod1.1.light)
anova.p <- round(anova$`Pr(>Chisq)`[2], 2)
anova.dAIC <- round(as.numeric(anova$AIC[2] - anova$AIC[1]), 2)
AIC <- round(as.numeric(anova$AIC[2]), 2)
BIC <- round(as.numeric(anova$BIC[2]), 2)

list <- c(Model, Variable, anova.p, anova.dAIC, AIC, BIC)
AIC.TABLE <- rbind(AIC.TABLE, list)
rm(mod1.1, mod1.1.light)

# CLEAN & SORT
#-------------

# remove first line full of NA's
AIC.TABLE <- AIC.TABLE[-1,]
AIC.TABLE$d.AIC <- NA

# dAIC
AIC.TABLE$AIC <- as.numeric(AIC.TABLE$AIC)
AIC.min <- AIC.TABLE$AIC[which.min(AIC.TABLE$AIC)]

for(i in (1:nrow(AIC.TABLE))){

  AIC.TABLE$d.AIC[i] <- round(AIC.TABLE$AIC[i] - AIC.min, 2)

}

AIC.TABLE$d.AIC <- as.numeric(AIC.TABLE$d.AIC)

# SORT
AIC.TABLE <- AIC.TABLE[order(AIC.TABLE$d.AIC),]
kable(AIC.TABLE)

rm(AIC.TABLE, AIC, AIC.min, i, list, Model, Variable, anova.dAIC, anova.p, BIC, anova)
#-------------------------------------------------------------------------------------------------------------

# BEST MODEL
#-----------
mod05.22 <- lmer(log(DAMAGES) ~ TREA_LIGHT * SPECIES + (1|STU.SI) + (1|LABEL), data = SUBSET)
qqnorm(residuals(mod05.22))
qqline(residuals(mod05.22))

# PRINT
`mod05.22.tbl` <- tbl_regression(mod05.22, 
                                intercept = T,
                                pvalue_fun = ~ style_pvalue(.x, digits = 3),
                                estimate_fun = ~ style_number(.x, digits = 3)) %>%
  
  # ADD COLUMNS
  modify_column_unhide(column = estimate) %>%
  modify_column_unhide(column = std.error) %>%
  modify_spanning_header(
    c(estimate, std.error, ci) ~ 
      "**Florivory severity ~ Light * Plant Sp. + (1|Study site) + (1|Label)**")  %>%

  # ADD SIGNIFICANCE LEVELS
  add_global_p() %>%
  # add_significance_stars(hide_p = FALSE, pattern = "{p.value}{stars}") %>%
    
  # ADD BOLD & ITALIC
  bold_labels() %>%
  italicize_levels()

knit_print(mod05.22.tbl)
# print(mod05.22.tbl)

# gtsave(as_gt(`mod05.22.tbl`),
#        file = file.path(paste0(HOME,"/mod05.22.tbl.png")))

rm(`mod05.22.tbl`)

#-------------------------------------------------------------------------------------------------------------

# POWER SIMULATION
#-----------------

nsim <- 10000

SUBSET$SPECIES <- as.factor(SUBSET$SPECIES)
n.level <- nlevels(SUBSET$SPECIES)
PLANT.LS <- levels(SUBSET$SPECIES)

# SIMULATION
bsim <- sim(mod05.22, n.sim = nsim)

# CALCULATE EFFECT SIZE
#----------------------

# EMPTY MATRIX
effmat <- matrix(ncol = nsim, nrow = n.level)
effmat[1,] <- bsim@fixef[, "TREA_LIGHTLIT"]

# FOR LOOP
for(i in (2:n.level)){

  # i <- 2

  effmat[i,] <- bsim@fixef[, "TREA_LIGHTLIT"] +
                bsim@fixef[, paste0("TREA_LIGHTLIT:SPECIES", levels(SUBSET$SPECIES)[i])]
}

# CHECK COEFFICIENTS
CI.FLO.SEV <- apply(effmat, 1, quantile, probs = c(0.05, 0.5, 0.95))
CI.FLO.SEV <- cbind(rep("FLO.SEV", 3), CI.FLO.SEV)
CI.FLO.SEV <- cbind(c(0.05, 0.5, 0.95), CI.FLO.SEV)

kable(CI.FLO.SEV)

rm(mod05.22, bsim, effmat, i, nsim)

#-------------------------------------------------------------------------------------------------------------

# MERGE MATRIX
#--------------
CI <- CI.FLO.SEV
colnames(CI) <- c("Level", "DAMAGES", PLANT.LS)
rownames(CI) <- NULL

CI <- as.data.frame(CI)
CI$Level <- as.numeric(CI$Level)

CI <- CI[order(CI$Level),]

# FORMAT CI
#----------

CI.coef <- data.frame(
  "i.damages" = 9999,
  "i.species" = 9999,
  "i.2.5" = 9999,
  "i.50" = 9999,
  "i.97.5" = 9999,
  "i.significant" = 9999)

for(i in PLANT.LS){ 
  
  # i <- "Malva moschata"
  
  i.CI.coef <- CI.coef[1,]
  i.2.5 <- CI[1, i]
  i.50 <- CI[2, i]
  i.97.5 <- CI[3, i]
  
  i.species <- i
  i.damages <- unique(CI$DAMAGES)
  
  i.significant <- 0

  i.CI.coef <- cbind(i.species, i.damages, i.2.5, i.50, i.97.5, i.significant)
  CI.coef <- rbind(CI.coef, i.CI.coef)

}

# REMOVE FIRST LINE FULL OF NA's
CI.coef <- CI.coef[-1,]

# FORMAT
CI.coef$i.2.5 <- as.numeric(CI.coef$i.2.5)
CI.coef$i.50 <- as.numeric(CI.coef$i.50)
CI.coef$i.97.5 <- as.numeric(CI.coef$i.97.5)

# SIGNIFICANT IF IT TOUCH THE LINE
for(i in (1:nrow(CI.coef))){
  
  # i <- 12
  
  ifelse(
    
    # ARGUMENT
    {(CI.coef$i.97.5[i] < 0 & CI.coef$i.2.5[i] < 0) | 
     (CI.coef$i.97.5[i] > 0 & CI.coef$i.2.5[i] > 0)},
    
    # IF YES
    CI.coef$i.significant[i] <- 1,
   
    # IF NO
    CI.coef$i.significant[i] <- 0)  
}

rm(CI, CI.FLO.SEV, i.CI.coef)
rm(i, i.2.5, i.50, i.97.5, i.damages, i.significant, i.species, PLANT.LS, n.level)

#-------------------------------------------------------------------------------------------------------------

# SEGMENT PLOT
#-------------

`05.22_CI.FLO.SEV` <- ggplot() +
  
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_linerange(
    data = CI.coef[CI.coef$i.damages == "FLO.SEV",],
    aes(
      x = i.species,
      ymin = i.2.5,
      ymax = i.97.5,
      color = i.species),
    size = 4,
    alpha = 0.5,
    position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "FLO.SEV",],
    aes(
      x = i.species,
      y = i.50,
      color = i.species),
      shape = 18,
      size = 8,
      position = position_dodge(width = 0.5)) +
  geom_point(
    data = CI.coef[CI.coef$i.damages == "FLO.SEV" & CI.coef$i.significant == "0",],
    aes(
      x = i.species,
      y = i.50),
    color = "white",
    shape = 18,
    size = 6,
    position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_classic() +
  labs(
    y = "Estimate",
    x = "Species",
    title = "Severity of eaten flowers") +
  scale_colour_manual(
    values = COLOR.PALETTE) +
  scale_y_continuous(
    limits = c(-1.5, 1.5)) +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 10, face = "bold"),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.line = element_blank(),
    # axis.text.y = element_text(size = 8, angle = 0, hjust = 0.5, face = "italic"),
    axis.title.x = element_text(size = 8, face = "bold"),
    axis.text.x = element_text(size = 8))

# plot(`05.22_CI.FLO.SEV`)

# SAVE
# ggsave(filename = paste0("05.22_CI.FLO.SEV.jpeg"),
#          plot = `05.22_CI.FLO.SEV`, path = HOME,
#          height = 8, width = 16, units = "cm")

rm(CI.coef, THRESHOLD, SUBSET, COLOR.PALETTE)

##############################################################################################################

# FINAL PLOT
#-----------

`04_HERBIVORY_IN_SITU` <- grid.arrange(`05.11_CI.HERB.ABS`, 
                                       `05.12_CI.HERB.SEV`, 
                                       `05.21_CI.FLO.ABS`, 
                                       `05.22_CI.FLO.SEV`, nrow = 1, widths = c(1.5,1,1,1))

rm(`04_HERBIVORY_IN_SITU`, `05.11_CI.HERB.ABS`, `05.12_CI.HERB.SEV`, `05.21_CI.FLO.ABS`, `05.22_CI.FLO.SEV`)

```

# THE END